---
title: "DataLoad_and_optimization_PhenotypingJuly17"
output: html_document
---

#Loading data from MS Access database

--------------------------------------------------------------VERY IMPORTANT!!!!!!!!!!!!!!
Steps to use, assuming 32 bit Access on windows 

Select 32 bit R (is just a setting in R studio)
search on windows for Set up ODBC data sources (32 bit)
Go to System DSN>Add
Choose Driver do Microsoft Access (*.mdb) > Finish
Data source name: ProjecnameAcc
Description: ProjectnameAcc
Make sure to actually select the database > OK
Now I could run the code that I liked

channel <- odbcConnect("ProjectnameAcc")
Table1Dat <- sqlFetch(channel, "Table1")

##Load Light Tables

```{r setup, include=FALSE}
#install.packages("RODBC")
library(RODBC)

library(readr)
hemodynamics_source_name_codes <- read_delim("C:/BIG FILES/Phenotyping/hemodynamics_source-name_codes.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)


for (i in 8:16){
  if (i<10) {
    # Connect to Access db  
    channel <- odbcConnect (paste("Hemodynamics0", i, sep=""))
    # Load tables
    tablename<-(paste("Text0", i, sep=""))
    assign( tablename,sqlFetch(channel, "Text"))
    tablename<-(paste("InfusionDrugs0", i, sep=""))
    assign( tablename,sqlFetch(channel, "InfusionDrugs"))
    tablename<-(paste("Events0", i, sep=""))
    assign( tablename,sqlFetch(channel, "Events"))
    tablename<-(paste("Date0", i, sep=""))
    assign( tablename,sqlFetch(channel, "Date"))
    tablename<-(paste("Combo0", i, sep=""))
    assign( tablename,sqlFetch(channel, "Combo"))
    tablename<-(paste("BolusDrugs0", i, sep=""))
    assign( tablename,sqlFetch(channel, "BolusDrugs"))
    tablename<-(paste("InfusionDrugs0", i, sep=""))
    assign( tablename,sqlFetch(channel, "InfusionDrugs"))
  
  }
  else{
    # Connect to Access db
    channel <- odbcConnect (paste("Hemodynamics", i, sep=""))
    # Load tables
    tablename<-(paste("Text", i, sep=""))
    assign( tablename,sqlFetch(channel, "Text"))
    tablename<-(paste("InfusionDrugs", i, sep=""))
    assign( tablename,sqlFetch(channel, "InfusionDrugs"))
    tablename<-(paste("Events", i, sep=""))
    assign( tablename,sqlFetch(channel, "Events"))
    tablename<-(paste("Date", i, sep=""))
    assign( tablename,sqlFetch(channel, "Date"))
    tablename<-(paste("Combo", i, sep=""))
    assign( tablename,sqlFetch(channel, "Combo"))
    tablename<-(paste("BolusDrugs", i, sep=""))
    assign( tablename,sqlFetch(channel, "BolusDrugs"))
    tablename<-(paste("InfusionDrugs", i, sep=""))
    assign( tablename,sqlFetch(channel, "InfusionDrugs"))
    }
}

```

##Load Heavy Tables  

```{r}
library(RODBC)

for (i in 16){
  if (i<10) {
  # Connect to Access db  
  channel <- odbcConnect (paste("Hemodynamics0", i, sep=""))
  # Load tables
    tablename<-(paste("Vitalsigns0", i, sep=""))
    assign( tablename,sqlFetch(channel, "Vitalsigns"))
  
  }
  else{
    # Connect to Access db
    channel <- odbcConnect (paste("Hemodynamics", i, sep=""))
    # Load tables
    tablename<-(paste("Vitalsigns", i, sep=""))
    assign( tablename,sqlFetch(channel, "Vitalsigns"))
    }
}
```

#Cleaning and optimizing the data

This chunk is removing not used columns and mapping the BP tags to a numerical code so the final dataset is lighter.

```{r}


dropList <- c("ItemID","Label","Units","Priority","Device_Name","Port#","Display_Value","Valid","User_Invalid","Limits_Invalid","Value_Questionable")
HDC_source_code<- hemodynamics_source_name_codes[,c(3,4)]

Vitalsigns08 <- Vitalsigns08[, !colnames(Vitalsigns08) %in% dropList]
Vitalsigns08$`Port#`<-NULL
Vitalsigns08<- merge(Vitalsigns08,  HDC_source_code, by='Source_Name')
Vitalsigns08$Source_Name<-NULL

Vitalsigns09 <- Vitalsigns09[, !colnames(Vitalsigns09) %in% dropList]
Vitalsigns09$`Port#`<-NULL
Vitalsigns09<- merge(Vitalsigns09,  HDC_source_code, by='Source_Name')
Vitalsigns09$Source_Name<-NULL

Vitalsigns10 <- Vitalsigns10[, !colnames(Vitalsigns10) %in% dropList]
Vitalsigns10$`Port#`<-NULL
Vitalsigns10<- merge(Vitalsigns10,  HDC_source_code, by='Source_Name')
Vitalsigns10$Source_Name<-NULL

Vitalsigns11 <- Vitalsigns11[, !colnames(Vitalsigns11) %in% dropList]
Vitalsigns11$`Port#`<-NULL
Vitalsigns11<- merge(Vitalsigns11,  HDC_source_code, by='Source_Name')
Vitalsigns11$Source_Name<-NULL

Vitalsigns12 <- Vitalsigns12[, !colnames(Vitalsigns12) %in% dropList]
Vitalsigns12$`Port#`<-NULL
Vitalsigns12<- merge(Vitalsigns12,  HDC_source_code, by='Source_Name')
Vitalsigns12$Source_Name<-NULL

Vitalsigns13 <- Vitalsigns13[, !colnames(Vitalsigns13) %in% dropList]
Vitalsigns13$`Port#`<-NULL
Vitalsigns13<- merge(Vitalsigns13,  HDC_source_code, by='Source_Name')
Vitalsigns13$Source_Name<-NULL

Vitalsigns14 <- Vitalsigns14[, !colnames(Vitalsigns14) %in% dropList]
Vitalsigns14$`Port#`<-NULL
Vitalsigns14<- merge(Vitalsigns14,  HDC_source_code, by='Source_Name')
Vitalsigns14$Source_Name<-NULL

Vitalsigns15 <- Vitalsigns15[, !colnames(Vitalsigns15) %in% dropList]
Vitalsigns15$`Port#`<-NULL
Vitalsigns15<- merge(Vitalsigns15,  HDC_source_code, by='Source_Name')
Vitalsigns15$Source_Name<-NULL

Vitalsigns16 <- Vitalsigns16[, !colnames(Vitalsigns16) %in% dropList]
Vitalsigns16$`Port#`<-NULL
Vitalsigns16<- merge(Vitalsigns16,  HDC_source_code, by='Source_Name')
Vitalsigns16$Source_Name<-NULL


```



