---
title: "Phenotyoing_Demographic_Analysis"
output: html_document
author: "Miguel Angel Armengol de la Hoz"
date: "27 de febrero de 2018"
toc: TRUE
---


# Environment

```{r}
library(dplyr)
library(summarytools)
library(readr)
```


```{r setup, include=FALSE}


#load("C:/BIG FILES/Phenotyping/HemodynamicProjectsDatasetFeb18.RData")

##IMPORTANT
#before converting date, run: 
Sys.setlocale("LC_ALL","English")

load("C:/BIG FILES/Phenotyping/STS.All.Status.Uni.v3.Rda")
STS_All_Status_Uni <- STS.All.Status.Uni.v3


STS_All_Status_Uni$Surgery_Date<-as.Date(STS_All_Status_Uni$Surgery_Date, format = "%d-%b-%y")

STS_2_73_July_2011_Jun_2014 <- read_delim("C:/BIG FILES/Phenotyping/new STS Generator and README Feb18/STS_2_73_July_2011_Jun_2014.csv", 
     ";", escape_double = FALSE, col_types = cols(Admission_Date = col_date(format = "%m/%d/%y"), 
         Discharge_Date = col_date(format = "%m/%d/%y"), 
         Surgery_Date = col_date(format = "%m/%d/%y")), 
     trim_ws = TRUE)

STS_2_81_July_2014_June_2017 <- read_delim("C:/BIG FILES/Phenotyping/new STS Generator and README Feb18/STS_2_81_July_2014_June_2017.csv", 
    ";", escape_double = FALSE, col_types = cols(Admission_Date = col_date(format = "%m/%d/%y"), 
        Discharge_Date = col_date(format = "%m/%d/%y"), 
        Surgery_Date = col_date(format = "%m/%d/%y")), 
    trim_ws = TRUE)

library(readxl)
data_superficial_wound_270_281_July2011_Jun_2014 <- read_excel("C:/BIG FILES/Phenotyping/new STS Generator and README Feb18/Bala_HgbA1C data update with superficial wound _270_281_dec 2016.xlsx", 
    col_types = c("text", "date", "date", 
        "date", "numeric", "numeric", "numeric", 
        "text", "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "text", "numeric", "text", "numeric", 
        "numeric", "numeric", "numeric", 
        "text", "numeric", "text", "text", 
        "text", "text", "numeric", "text", 
        "text", "text", "numeric", "numeric", 
        "text", "numeric", "numeric", "numeric", 
        "numeric", "numeric", "text", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "text", "text", "text", 
        "text", "text", "text", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "text", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "text"))

data_superficial_wound_270_281_July2014_Dec_2016 <- read_excel("C:/BIG FILES/Phenotyping/new STS Generator and README Feb18/Bala_HgbA1C data update with superficial wound _270_281_dec 2016.xlsx", sheet = "Jul 14-Dec16", col_types = c("text", 
"date", "date", "date", "numeric", 
"text", "numeric", "text", "numeric", 
"numeric", "numeric", "numeric", 
"numeric", "numeric", "numeric", 
"numeric", "numeric", "numeric", 
"numeric", "numeric", "numeric", 
"numeric", "text", "numeric", "text", 
"text", "text", "text", "text", "text", 
"text", "numeric", "text", "numeric", 
"text", "text", "text", "numeric", 
"text", "text", "text", "text", "text", 
"text", "text", "text", "text", "text", 
"text", "text", "numeric", "numeric", 
"text", "numeric", "text", "text", 
"text", "text", "text", "numeric", 
"numeric", "numeric", "numeric", 
"numeric", "text", "text", "text", 
"text", "text", "text", "numeric", 
"numeric", "numeric", "numeric", 
"numeric", "numeric", "numeric", 
"numeric", "numeric", "text", "text", 
"numeric", "numeric", "numeric", 
"numeric", "numeric", "numeric", 
"numeric", "numeric", "text"))

```

# Creating final uncorrupted full dataset

There are still some duplicated patients we need to remove

```{r}
library(dplyr)
library(plyr)
#In the plyr package there is a function rbind.fill that will merge data.frames and introduce NA for empty cells

#the original dataset needs to be filtered until the next one is starting.
STS_All_Status_Uni_Jan_2008_Jun_2011<-subset(STS_All_Status_Uni, format(as.Date(Surgery_Date))<='2011-06-31')


STS_full_dataset<-rbind.fill(STS_All_Status_Uni_Jan_2008_Jun_2011, STS_2_73_July_2011_Jun_2014,STS_2_81_July_2014_June_2017)

#formating dates properly for the left join
#to be runned only the first time
STS_full_dataset$Surgery_Date<-format(STS_full_dataset$Surgery_Date, "%Y-%m-%d")
data_superficial_wound_270_281_July2011_Jun_2014$Surgery_Date<-format(data_superficial_wound_270_281_July2011_Jun_2014$Surgery_Date, "%Y-%m-%d")
data_superficial_wound_270_281_July2014_Dec_2016$Surgery_Date<-format(data_superficial_wound_270_281_July2014_Dec_2016$Surgery_Date, "%Y-%m-%d")

#Cleaning PostOpSternalSuperficialInfect in data_superficial_wound_270_281_July2011_Jun_2014
data_superficial_wound_270_281_July2011_Jun_2014$PostOpSternalSuperficialInfect[is.na(data_superficial_wound_270_281_July2011_Jun_2014$PostOpSternalSuperficialInfect)]<-0
data_superficial_wound_270_281_July2011_Jun_2014$PostOpSternalSuperficialInfect[data_superficial_wound_270_281_July2011_Jun_2014$PostOpSternalSuperficialInfect=='No']<-0
data_superficial_wound_270_281_July2011_Jun_2014$PostOpSternalSuperficialInfect[data_superficial_wound_270_281_July2011_Jun_2014$PostOpSternalSuperficialInfect=='Yes']<-1

#Cleaning PostOpSternalSuperficialInfect in data_superficial_wound_270_281_July2014_Dec_2016

data_superficial_wound_270_281_July2014_Dec_2016$PostOpSternalSuperficialInfect[is.na(data_superficial_wound_270_281_July2014_Dec_2016$PostOpSternalSuperficialInfect)]<-0
data_superficial_wound_270_281_July2014_Dec_2016$PostOpSternalSuperficialInfect[data_superficial_wound_270_281_July2014_Dec_2016$PostOpSternalSuperficialInfect=='No']<-0
data_superficial_wound_270_281_July2014_Dec_2016$PostOpSternalSuperficialInfect[data_superficial_wound_270_281_July2014_Dec_2016$PostOpSternalSuperficialInfect=='Yes, within 30 days of procedure']<-1

#performing left joins with the datasets containing wounds info.
STS_full_dataset<-left_join(STS_full_dataset, subset(data_superficial_wound_270_281_July2011_Jun_2014,
select = c("Surgery_Date","Patient_ID","PostOpSternalSuperficialInfect","PostOpSternalMediastinitis","Infect_Thoracotomy","Infect_Leg")), 
                            by=c("Surgery_Date","Patient_ID"))

STS_full_dataset<-left_join(STS_full_dataset,  subset(data_superficial_wound_270_281_July2014_Dec_2016,
select = c("Surgery_Date","Patient_ID","PostOpSternalSuperficialInfect","PostOpCannulationSite","PostOpConduitHarvest")),
                            by=c("Surgery_Date","Patient_ID"))


#Formating dates

STS_full_dataset$DateOfDeath<-as.Date(STS_full_dataset$DateOfDeath, "%d-%B-%y")
STS_full_dataset$Surgery_Date<-as.Date(STS_full_dataset$Surgery_Date, "%Y-%m-%d")
STS_full_dataset$Admission_Date<-as.Date(STS_full_dataset$Admission_Date, "%Y-%m-%d")
STS_full_dataset$Discharge_Date<-as.Date(STS_full_dataset$Discharge_Date, "%Y-%m-%d")

write.table(STS_full_dataset,'STS_full_dataset.txt')

#AIMS dataset goes up to June 2016
STS_full_dataset_2008_2016<-subset(STS_full_dataset, format(as.Date(Surgery_Date))<='2016-06-31')




```



 
# Removing duplications

There are still some duplicated patients we need to remove

```{r}
STS_full_dataset_2008_2016 <- STS_full_dataset_2008_2016[ ! rownames(STS_full_dataset_2008_2016) %in% 
                which( duplicated(STS_full_dataset_2008_2016$Patient_ID)), ]
```


# STS

## Columns removing

```{r}
#some columns are causing problems, we remove them for the final dataset
#STS_full_dataset_2008_2016$actualsurgery<-NULL
STS_full_dataset_2008_2016$Comments<-NULL

#we remove columns we don't need
STS_full_dataset_2008_2016$morbmort<-NULL
STS_full_dataset_2008_2016$morbmortbinary<-NULL
STS_full_dataset_2008_2016$Surgery_Type_Code<-NULL
# STS_full_dataset_2008_2016$Surgery_Type_Descript<-NULL
STS_full_dataset_2008_2016$Num_Distals<-NULL

#some .bin columns might be incomplete so we remove them all
BINcolumns<-grep("bin", names(STS_full_dataset_2008_2016), value = TRUE)

for (name in names(STS_full_dataset_2008_2016)){
if (name %in%  BINcolumns){
  STS_full_dataset_2008_2016[name]<-NULL
  }
  
}


write.csv(STS_full_dataset_2008_2016,'STS_full_dataset_2008_2016.csv')
```

## Exclusion Criteria

```{r}
#we exclude those patients not in our study Category and status
library(dplyr)
STS_filtered<-STS_full_dataset_2008_2016 %>%
#filter(grepl('CAB',Category)) %>%
filter(!grepl('Cancelled case',Category)) %>%
filter(grepl('Urgen|Elective', Status))



```

## Data Mapping STS dataset

### Exposures

```{r}
#we merge CAB categories

#Combine CABG and CABG +Other,
# Combine VALVE and VALVE + other
# Combine CABG +Valve and CABG+Valve+other

#Cleaning Diabetes
STS_filtered$Diabetes[is.na(STS_filtered$Diabetes)]<-0
STS_filtered$Diabetes[STS_filtered$Diabetes=='']<-0
STS_filtered$Diabetes[STS_filtered$Diabetes=='No']<-0
STS_filtered$Diabetes[STS_filtered$Diabetes=='Yes']<-1

#Cleaning RFDyslipidemia
STS_filtered$RFDyslipidemia[is.na(STS_filtered$RFDyslipidemia)]<-0
STS_filtered$RFDyslipidemia[STS_filtered$RFDyslipidemia=='']<-0
STS_filtered$RFDyslipidemia[STS_filtered$RFDyslipidemia=='No']<-0
STS_filtered$RFDyslipidemia[STS_filtered$RFDyslipidemia=='Unknown']<-0
STS_filtered$RFDyslipidemia[STS_filtered$RFDyslipidemia=='Yes']<-1

#Cleaning ChronicLungDisease
STS_filtered$ChronicLungDisease[is.na(STS_filtered$ChronicLungDisease)]<-0
STS_filtered$ChronicLungDisease[STS_filtered$ChronicLungDisease=='Lung disease documen']<-1
STS_filtered$ChronicLungDisease[STS_filtered$ChronicLungDisease=='Mild']<-1             
STS_filtered$ChronicLungDisease[STS_filtered$ChronicLungDisease=='Moderate']<-1
STS_filtered$ChronicLungDisease[STS_filtered$ChronicLungDisease=='Severe']<-1
STS_filtered$ChronicLungDisease[STS_filtered$ChronicLungDisease=='No']<-0
STS_filtered$ChronicLungDisease[STS_filtered$ChronicLungDisease=='']<-0 
STS_filtered$ChronicLungDisease[STS_filtered$ChronicLungDisease=='Unknown']<-0

#Cleaning Dialysis
STS_filtered$Dialysis[STS_filtered$Dialysis=='No']<-0
STS_filtered$Dialysis[STS_filtered$Dialysis=='']<-0
STS_filtered$Dialysis[STS_filtered$Dialysis=='Yes']<-1
STS_filtered$Dialysis[is.na(STS_filtered$Dialysis)]<-0

#Cleaning PreOpMedBetaBlockers
STS_filtered$PreOpMedBetaBlockers[is.na(STS_filtered$PreOpMedBetaBlockers)]<-0
STS_filtered$PreOpMedBetaBlockers[STS_filtered$PreOpMedBetaBlockers=='']<-0
STS_filtered$PreOpMedBetaBlockers[STS_filtered$PreOpMedBetaBlockers=='Contraindicated']<-0
STS_filtered$PreOpMedBetaBlockers[STS_filtered$PreOpMedBetaBlockers=='Contraindicated / 0t Indicated']<-0
STS_filtered$PreOpMedBetaBlockers[STS_filtered$PreOpMedBetaBlockers=='Contraindicated / Not Indicated']<-0
STS_filtered$PreOpMedBetaBlockers[STS_filtered$PreOpMedBetaBlockers=='No']<-0
STS_filtered$PreOpMedBetaBlockers[STS_filtered$PreOpMedBetaBlockers=='']<-0
STS_filtered$PreOpMedBetaBlockers[STS_filtered$PreOpMedBetaBlockers=='Yes']<-1
STS_filtered$PreOpMedBetaBlockers<-as.factor(STS_filtered$PreOpMedBetaBlockers)


#Cleaning PreOpMedInotropes
STS_filtered$PreOpMedInotropes[is.na(STS_filtered$PreOpMedInotropes)]<-0
STS_filtered$PreOpMedInotropes[STS_filtered$PreOpMedInotropes=='']<-0
STS_filtered$PreOpMedInotropes[STS_filtered$PreOpMedInotropes=='Contraindicated']<-0
STS_filtered$PreOpMedInotropes[STS_filtered$PreOpMedInotropes=='Contraindicated / 0t Indicated']<-0
STS_filtered$PreOpMedInotropes[STS_filtered$PreOpMedInotropes=='Contraindicated / Not Indicated']<-0
STS_filtered$PreOpMedInotropes[STS_filtered$PreOpMedInotropes=='No']<-0
STS_filtered$PreOpMedInotropes[STS_filtered$PreOpMedInotropes=='Yes']<-1
STS_filtered$PreOpMedInotropes<-as.factor(STS_filtered$PreOpMedInotropes)

#Cleaning PreOpMedSteroids
STS_filtered$PreOpMedSteroids[is.na(STS_filtered$PreOpMedSteroids)]<-0
STS_filtered$PreOpMedSteroids[STS_filtered$PreOpMedSteroids=='']<-0
STS_filtered$PreOpMedSteroids[STS_filtered$PreOpMedSteroids=='Contraindicated']<-0
STS_filtered$PreOpMedSteroids[STS_filtered$PreOpMedSteroids=='Contraindicated / 0t Indicated']<-0
STS_filtered$PreOpMedSteroids[STS_filtered$PreOpMedSteroids=='Contraindicated / Not Indicated']<-0
STS_filtered$PreOpMedSteroids[STS_filtered$PreOpMedSteroids=='No']<-0
STS_filtered$PreOpMedSteroids[STS_filtered$PreOpMedSteroids=='Yes']<-1
STS_filtered$PreOpMedSteroids<-as.factor(STS_filtered$PreOpMedSteroids)

#Cleaning PreOpMedAspirin
STS_filtered$PreOpMedAspirin[is.na(STS_filtered$PreOpMedAspirin)]<-0
STS_filtered$PreOpMedAspirin[STS_filtered$PreOpMedAspirin=='']<-0
STS_filtered$PreOpMedAspirin[STS_filtered$PreOpMedAspirin=='Contraindicated']<-0
STS_filtered$PreOpMedAspirin[STS_filtered$PreOpMedAspirin=='Contraindicated / 0t Indicated']<-0
STS_filtered$PreOpMedAspirin[STS_filtered$PreOpMedAspirin=='Contraindicated / Not Indicated']<-0
STS_filtered$PreOpMedAspirin[STS_filtered$PreOpMedAspirin=='No']<-0
STS_filtered$PreOpMedAspirin[STS_filtered$PreOpMedAspirin=='Yes']<-1

#Cleaning PreOpMedLipidLowering 
# AKA statins
STS_filtered$PreOpMedLipidLowering[is.na(STS_filtered$PreOpMedLipidLowering)]<-0
STS_filtered$PreOpMedLipidLowering[STS_filtered$PreOpMedLipidLowering=='Contraindicated']<-0
STS_filtered$PreOpMedLipidLowering[STS_filtered$PreOpMedLipidLowering=='Contraindicated / 0t Indicated']<-0
STS_filtered$PreOpMedLipidLowering[STS_filtered$PreOpMedLipidLowering=='Contraindicated / Not Indicated']<-0
STS_filtered$PreOpMedLipidLowering[STS_filtered$PreOpMedLipidLowering=='No']<-0
STS_filtered$PreOpMedLipidLowering[STS_filtered$PreOpMedLipidLowering=='Yes']<-1
STS_filtered$PreOpMedLipidLowering[STS_filtered$PreOpMedLipidLowering=='Unknown']<-0
STS_filtered$PreOpMedLipidLowering[STS_filtered$PreOpMedLipidLowering=='']<-0
STS_filtered$PreOpMedLipidLowering<-as.factor(STS_filtered$PreOpMedLipidLowering)

#Cleaning TobaccoUse
STS_filtered$TobaccoUse[is.na(STS_filtered$TobaccoUse)]<-0
STS_filtered$TobaccoUse[STS_filtered$TobaccoUse=='']<- 0
STS_filtered$TobaccoUse<-as.character(STS_filtered$TobaccoUse)
STS_filtered$TobaccoUse[STS_filtered$TobaccoUse=='Current every day smoker'|
STS_filtered$TobaccoUse=='Current some day smoker'|
STS_filtered$TobaccoUse=='Former smoker' |
STS_filtered$TobaccoUse=='Smoker, current status (frequency) unknown']<- 1
STS_filtered$TobaccoUse[STS_filtered$TobaccoUse=='Never smoker']<- 0
STS_filtered$TobaccoUse[STS_filtered$TobaccoUse=='Smoking status unknown']<-0

#Cleaning CHF
STS_filtered$CHF[is.na(STS_filtered$CHF)]<-0
STS_filtered$CHF[STS_filtered$CHF=='']<-0
STS_filtered$CHF[STS_filtered$CHF=='No']<-0
STS_filtered$CHF[STS_filtered$CHF=='Yes']<-1

#Cleaning HeartFailure2wks
STS_filtered$HeartFailure2wks[is.na(STS_filtered$HeartFailure2wks)]<-0
STS_filtered$HeartFailure2wks[STS_filtered$HeartFailure2wks=='']<-0
STS_filtered$HeartFailure2wks[STS_filtered$HeartFailure2wks=='No']<-0
STS_filtered$HeartFailure2wks[STS_filtered$HeartFailure2wks=='Yes']<-1

#Cleaning Hypertension
STS_filtered$Hypertension[is.na(STS_filtered$Hypertension)]<-0
STS_filtered$Hypertension[STS_filtered$Hypertension=='']<-0
STS_filtered$Hypertension[STS_filtered$Hypertension=='No']<-0
STS_filtered$Hypertension[STS_filtered$Hypertension=='Yes']<-1

#Cleaning RFHypertension
STS_filtered$RFHypertension[is.na(STS_filtered$RFHypertension)]<-0
STS_filtered$RFHypertension[STS_filtered$RFHypertension=='']<-0
STS_filtered$RFHypertension[STS_filtered$RFHypertension=='Unknown']<-0
STS_filtered$RFHypertension[STS_filtered$RFHypertension=='No']<-0
STS_filtered$RFHypertension[STS_filtered$RFHypertension=='Yes']<-1

#Cleaning PreviousMI 
STS_filtered$PreviousMI[is.na(STS_filtered$PreviousMI)]<-0
STS_filtered$PreviousMI[STS_filtered$PreviousMI=='']<-0
STS_filtered$PreviousMI[STS_filtered$PreviousMI=='No']<-0
STS_filtered$PreviousMI[STS_filtered$PreviousMI=='Yes']<-1

#Cleaning PriorMI 
STS_filtered$PriorMI[is.na(STS_filtered$PriorMI)]<-0
STS_filtered$PriorMI[STS_filtered$PriorMI=='']<-0
STS_filtered$PriorMI[STS_filtered$PriorMI=='No']<-0
STS_filtered$PriorMI[STS_filtered$PriorMI=='Yes']<-1

#Drugs

#Cleaning PreOpMedACE_ARBInhibitors
STS_filtered$PreOpMedACE_ARBInhibitors[STS_filtered$PreOpMedACE_ARBInhibitors=='Contraindicated']<-0
STS_filtered$PreOpMedACE_ARBInhibitors[STS_filtered$PreOpMedACE_ARBInhibitors=='']<-0
STS_filtered$PreOpMedACE_ARBInhibitors[STS_filtered$PreOpMedACE_ARBInhibitors=='Contraindicated / 0t Indicated']<-0
STS_filtered$PreOpMedACE_ARBInhibitors[STS_filtered$PreOpMedACE_ARBInhibitors=='Contraindicated / Not Indicated']<-0
STS_filtered$PreOpMedACE_ARBInhibitors[STS_filtered$PreOpMedACE_ARBInhibitors=='No']<-0
STS_filtered$PreOpMedACE_ARBInhibitors[STS_filtered$PreOpMedACE_ARBInhibitors=='Yes']<-1
STS_filtered$PreOpMedACE_ARBInhibitors<-as.factor(STS_filtered$PreOpMedACE_ARBInhibitors)
STS_filtered$PreOpMedACE_ARBInhibitors[is.na(STS_filtered$PreOpMedACE_ARBInhibitors)]<-0

#Cleaning PreOpMedACEIARBI48hrs
STS_filtered$PreOpMedACEIARBI48hrs[STS_filtered$PreOpMedACEIARBI48hrs=='Contraindicated']<-0
STS_filtered$PreOpMedACEIARBI48hrs[STS_filtered$PreOpMedACEIARBI48hrs=='']<-0
STS_filtered$PreOpMedACEIARBI48hrs[STS_filtered$PreOpMedACEIARBI48hrs=='No']<-0
STS_filtered$PreOpMedACEIARBI48hrs[STS_filtered$PreOpMedACEIARBI48hrs=='Yes']<-1
STS_filtered$PreOpMedACEIARBI48hrs[is.na(STS_filtered$PreOpMedACEIARBI48hrs)]<-0
STS_filtered$PreOpMedACEIARBI48hrs<-as.factor(STS_filtered$PreOpMedACEIARBI48hrs)

```

### Outcomes

```{r}

#Cleaning Reop_Bleeding
STS_filtered$Reop_Bleeding[is.na(STS_filtered$Reop_Bleeding)]<-0

#Cleaning Infect_Sternum_Deep
STS_filtered$Infect_Sternum_Deep[is.na(STS_filtered$Infect_Sternum_Deep)]<-0
STS_filtered$Infect_Sternum_Deep[STS_filtered$Infect_Sternum_Deep=='']<-0
STS_filtered$Infect_Sternum_Deep[STS_filtered$Infect_Sternum_Deep=='No']<-0
STS_filtered$Infect_Sternum_Deep[STS_filtered$Infect_Sternum_Deep=='Yes']<-1

#Cleaning PostOpSternalMediastinitis
STS_filtered$PostOpSternalMediastinitis[is.na(STS_filtered$PostOpSternalMediastinitis)]<-0
STS_filtered$PostOpSternalMediastinitis[STS_filtered$PostOpSternalMediastinitis=='']<-0
STS_filtered$PostOpSternalMediastinitis[STS_filtered$PostOpSternalMediastinitis=='No']<-0
STS_filtered$PostOpSternalMediastinitis[STS_filtered$PostOpSternalMediastinitis=='Yes']<-1

#Cleaning Infect_Thoracotomy
STS_filtered$Infect_Thoracotomy[is.na(STS_filtered$Infect_Thoracotomy)]<-0
STS_filtered$Infect_Thoracotomy[STS_filtered$Infect_Thoracotomy=='']<-0
STS_filtered$Infect_Thoracotomy[STS_filtered$Infect_Thoracotomy=='No']<-0
STS_filtered$Infect_Thoracotomy[STS_filtered$Infect_Thoracotomy=='Yes']<-1

#Cleaning Infect_Leg
STS_filtered$Infect_Leg[is.na(STS_filtered$Infect_Leg)]<-0
STS_filtered$Infect_Leg[STS_filtered$Infect_Leg=='']<-0
STS_filtered$Infect_Leg[STS_filtered$Infect_Leg=='No']<-0
STS_filtered$Infect_Leg[STS_filtered$Infect_Leg=='Yes']<-1

#Cleaning PostOpSternalSuperficialInfect.x
STS_filtered$PostOpSternalSuperficialInfect.x[is.na(STS_filtered$PostOpSternalSuperficialInfect.x)]<-0
STS_filtered$PostOpSternalSuperficialInfect.x[STS_filtered$PostOpSternalSuperficialInfect.x=='']<-0
STS_filtered$PostOpSternalSuperficialInfect.x[STS_filtered$PostOpSternalSuperficialInfect.x=='No']<-0
STS_filtered$PostOpSternalSuperficialInfect.x[STS_filtered$PostOpSternalSuperficialInfect.x=='Yes']<-1

#Cleaning PostOpSternalSuperficialInfect.y
STS_filtered$PostOpSternalSuperficialInfect.y[is.na(STS_filtered$PostOpSternalSuperficialInfect.y)]<-0
STS_filtered$PostOpSternalSuperficialInfect.y[STS_filtered$PostOpSternalSuperficialInfect.y=='']<-0
STS_filtered$PostOpSternalSuperficialInfect.y[STS_filtered$PostOpSternalSuperficialInfect.y=='No']<-0
STS_filtered$PostOpSternalSuperficialInfect.y[STS_filtered$PostOpSternalSuperficialInfect.y=='Yes']<-1
STS_filtered$PostOpSternalSuperficialInfect.y<-as.numeric(STS_filtered$PostOpSternalSuperficialInfect.y)


#Cleaning PostOpDeepSternalMediastin
STS_filtered$PostOpDeepSternalMediastin[is.na(STS_filtered$PostOpDeepSternalMediastin)]<-0
STS_filtered$PostOpDeepSternalMediastin[STS_filtered$PostOpDeepSternalMediastin=='']<-0
STS_filtered$PostOpDeepSternalMediastin[STS_filtered$PostOpDeepSternalMediastin=='No']<-0
STS_filtered$PostOpDeepSternalMediastin[STS_filtered$PostOpDeepSternalMediastin=='Yes']<-1
STS_filtered$PostOpDeepSternalMediastin<-as.numeric(STS_filtered$PostOpDeepSternalMediastin)


#Cleaning PostOpCannulationSite
STS_filtered$PostOpCannulationSite[is.na(STS_filtered$PostOpCannulationSite)]<-0
STS_filtered$PostOpCannulationSite[STS_filtered$PostOpCannulationSite=='']<-0
STS_filtered$PostOpCannulationSite[STS_filtered$PostOpCannulationSite=='No']<-0
STS_filtered$PostOpCannulationSite[STS_filtered$PostOpCannulationSite=='Yes']<-1
STS_filtered$PostOpCannulationSite<-as.numeric(STS_filtered$PostOpCannulationSite)

#Cleaning PostOpConduitHarvest
STS_filtered$PostOpConduitHarvest[is.na(STS_filtered$PostOpConduitHarvest)]<-0
STS_filtered$PostOpConduitHarvest[STS_filtered$PostOpConduitHarvest=='']<-0
STS_filtered$PostOpConduitHarvest[STS_filtered$PostOpConduitHarvest=='No']<-0
STS_filtered$PostOpConduitHarvest[STS_filtered$PostOpConduitHarvest=='Yes, within 30 days of procedure']<-1
STS_filtered$PostOpConduitHarvest<-as.numeric(STS_filtered$PostOpConduitHarvest)

#Cleaning Neuro_Stroke_Permanent
STS_filtered$Neuro_Stroke_Permanent[is.na(STS_filtered$Neuro_Stroke_Permanent)]<-0
STS_filtered$Neuro_Stroke_Permanent[STS_filtered$Neuro_Stroke_Permanent=='']<-0
STS_filtered$Neuro_Stroke_Permanent[STS_filtered$Neuro_Stroke_Permanent=='No']<-0
STS_filtered$Neuro_Stroke_Permanent[STS_filtered$Neuro_Stroke_Permanent=='Yes']<-1

#Cleaning PostOpNeuroStrokePermanent
STS_filtered$PostOpNeuroStrokePermanent[is.na(STS_filtered$PostOpNeuroStrokePermanent)]<-0
STS_filtered$PostOpNeuroStrokePermanent[STS_filtered$PostOpNeuroStrokePermanent=='']<-0
STS_filtered$PostOpNeuroStrokePermanent[STS_filtered$PostOpNeuroStrokePermanent=='No']<-0
STS_filtered$PostOpNeuroStrokePermanent[STS_filtered$PostOpNeuroStrokePermanent=='Yes, embolic']<-1
STS_filtered$PostOpNeuroStrokePermanent[STS_filtered$PostOpNeuroStrokePermanent=='Yes, hemorrhagic']<-1

#Cleaning Pulm_Pneumonia
STS_filtered$Pulm_Pneumonia[is.na(STS_filtered$Pulm_Pneumonia)]<-0
STS_filtered$Pulm_Pneumonia[STS_filtered$Pulm_Pneumonia=='']<-0

#Cleaning Renal_Failure
STS_filtered$Renal_Failure[is.na(STS_filtered$Renal_Failure)]<-0
STS_filtered$Renal_Failure[STS_filtered$Renal_Failure=='']<-0

#Cleaning Oth_Tamponade
STS_filtered$Oth_Tamponade[is.na(STS_filtered$Oth_Tamponade)]<-0
STS_filtered$Oth_Tamponade[STS_filtered$Oth_Tamponade=='']<-0


#Cleaning Death
STS_filtered$Death[is.na(STS_filtered$Death)]<-0
STS_filtered$Death[STS_filtered$Death=='']<-0


#Cleaning Oth_AFib
STS_filtered$Oth_AFib[is.na(STS_filtered$Oth_AFib)]<-0
STS_filtered$Oth_AFib[STS_filtered$Oth_AFib=='']<-0


listVars<-c("Gender",
  "Age",
  "Category",
  
  #Background diseases
  "Diabetes",
  "RFDyslipidemia",
  "Hypertension_final",
  "Smoking",
  "Congestive_Heart_Failure",
  "Previous_myocardial_infarction",
  "ChronicLungDisease",
  "Dialysis",
  
  #Preoperative medications
  "PreOpMedBetaBlockers",
  "PreOpMedACEI_or_ARBs",
  "PreOpMedInotropes",
  "PreOpMedSteroids",
  "PreOpMedAspirin",
  "PreOpMedLipidLowering"
)

# # There are 9 patients always missing baseline variables we are going to remove them
# patientsmissingbaselinevars<-STS_filtered$Patient_ID[is.na(STS_filtered$Diabetes)]
# 
# STS_filtered<-STS_filtered[!STS_filtered$Patient_ID %in% patientsmissingbaselinevars, ]

# #we corect missing values
# #STS columns NA=NULL, In the rest NA=0
# 
# #we are going to store the columns id which contains the string 'STS' becasuse in these columns NA means unknown
# STScolumns<-grep("STS", names(STS_filtered), value = TRUE)
# #other Columns where NA means unknown
# STScolumns<-append(STScolumns, c('Diabetes', 'PreviousMI', 
#   
#   "PreOpMedBetaBlockers",
#   "PreOpMedACE_ARBInhibitors",
#   "PreOpMedInotropes",
#   "PreOpMedSteroids",
#   "PreOpMedAspirin",
#   "PreOpMedLipidLowering"))
# STScolumns<-which(names(STS_filtered) %in% (STScolumns))
# 
# #Columns where NA means unknown
# 
# STS_filtered$Diabetes[is.na(STS_filtered$Diabetes)]<-'Unknown'
# STS_filtered$ChronicLungDisease[is.na(STS_filtered$ChronicLungDisease)]<-'Unknown'
# STS_filtered$TobaccoUse[is.na(STS_filtered$TobaccoUse)]<-'Smoking status unknown'
# STS_filtered$RFDyslipidemia[is.na(STS_filtered$RFDyslipidemia)]<-'Unknown'



#For those columns where NA doesn't mean unknown replace NA with 0

# for (i in 1:length(colnames(STS_filtered))){
#   if (i %in% STScolumns){
#     
#   }
#   else(STS_filtered[,i][is.na(STS_filtered[,i])] <- 0)
# }

#convert character columns to factors
#charactercolumns<-sapply(STS_filtered, is.character)

#STS_filtered[charactercolumns] <- lapply(STS_filtered[charactercolumns], factor)
```

# Converting columns to the right format

```{r}
STS_filtered$PreOpMedACE_ARBInhibitors<-as.character(STS_filtered$PreOpMedACE_ARBInhibitors)
STS_filtered$PreOpMedBetaBlockers<-as.character(STS_filtered$PreOpMedBetaBlockers)
STS_filtered$PreOpMedLipidLowering<-as.character(STS_filtered$PreOpMedLipidLowering)
```


# Creating new columns with constant data for the period 2008-2016

```{r}
#AIMS dataset goes up to June 2016

#Creating Stroke column

STS_filtered['Stroke']<-NA

STS_filtered$Stroke<-if_else(
  format(as.Date(STS_filtered$Surgery_Date))<='2014-06-31',
  STS_filtered$Neuro_Stroke_Permanent ,
  STS_filtered$PostOpNeuroStrokePermanent
)

STS_filtered$Stroke[is.na(STS_filtered$Stroke)]<-0

#Creating Smoking column

STS_filtered['Smoking']<-NA

STS_filtered$Smoking<-if_else(
  format(as.Date(STS_filtered$Surgery_Date))<='2014-06-31',
  STS_filtered$RFCurrentRecentCigarette  ,
  as.integer(STS_filtered$TobaccoUse)
)
STS_filtered$Smoking[is.na(STS_filtered$Smoking)]<-0

#Creating Congestive_Heart_Failure column


STS_filtered['Congestive_Heart_Failure']<-NA

STS_filtered$Congestive_Heart_Failure<-if_else(
  format(as.Date(STS_filtered$Surgery_Date))<='2014-06-31',
  STS_filtered$CHF   ,
  STS_filtered$HeartFailure2wks
)
STS_filtered$Congestive_Heart_Failure[is.na(STS_filtered$Congestive_Heart_Failure)]<-0
#Creating Hypertension_final column



STS_filtered['Hypertension_final']<-NA

STS_filtered$Hypertension_final<-if_else(
  format(as.Date(STS_filtered$Surgery_Date))<='2014-06-31',
  STS_filtered$Hypertension    ,
  STS_filtered$RFHypertension 
)
STS_filtered$Hypertension_final[is.na(STS_filtered$Hypertension_final)]<-0
#Creating Previous_myocardial_infarction column




STS_filtered['Previous_myocardial_infarction']<-NA

STS_filtered$Previous_myocardial_infarction<-if_else(
  format(as.Date(STS_filtered$Surgery_Date))<='2014-06-31',
  STS_filtered$PreviousMI     ,
  STS_filtered$PriorMI 
)
STS_filtered$Previous_myocardial_infarction[is.na(STS_filtered$Previous_myocardial_infarction)]<-0

#Creating PreOpMedACEI_or_ARBs column



STS_filtered['PreOpMedACEI_or_ARBs']<-NA

STS_filtered$PreOpMedACEI_or_ARBs<-if_else(
  format(as.Date(STS_filtered$Surgery_Date))<='2011-06-31',
  STS_filtered$PreOpMedACE_ARBInhibitors     ,
  as.character(STS_filtered$PreOpMedACEIARBI48hrs) 
)
STS_filtered$PreOpMedACEI_or_ARBs[is.na(STS_filtered$PreOpMedACEI_or_ARBs)]<-0

#Creating Infection column

# Post-Op-Sternal-Superficial Wound Infection
# Short Name: CSternalSupInf

#PostOpDeepSternalMediastin only contains data from 2014
STS_filtered['Infection']<-NA

STS_filtered$Infection<-if_else(
format(as.Date(STS_filtered$Surgery_Date))<='2011-06-31',as.numeric(STS_filtered$Infect_Sternum_Deep) ,
    if_else(
    format(as.Date(STS_filtered$Surgery_Date))<='2014-06-31',
    if_else(STS_filtered$PostOpSternalSuperficialInfect.x+STS_filtered$Infect_Thoracotomy+ STS_filtered$PostOpSternalMediastinitis>0,1,0)  ,
    if_else(STS_filtered$PostOpSternalSuperficialInfect.y+STS_filtered$PostOpCannulationSite+ STS_filtered$PostOpConduitHarvest>0,1,0)
)
)

STS_filtered$Infection[is.na(STS_filtered$Infection)]<-0

#Cleaning
#STS_filtered$Deep_Sternal_Infection[is.na(STS_filtered$Deep_Sternal_Infection)]<-0
  
```

## Data Mapping STS new created columns

```{r}
#Cleaning Congestive_Heart_Failure
STS_filtered$Congestive_Heart_Failure[is.na(STS_filtered$Congestive_Heart_Failure)]<-0
STS_filtered$Congestive_Heart_Failure[STS_filtered$Congestive_Heart_Failure=='']<-0
STS_filtered$Congestive_Heart_Failure[STS_filtered$Congestive_Heart_Failure=='Unknown']<-0


#Cleaning Previous_myocardial_infarction
STS_filtered$Previous_myocardial_infarction[is.na(STS_filtered$Previous_myocardial_infarction)]<-0
STS_filtered$Previous_myocardial_infarction[STS_filtered$Previous_myocardial_infarction=='']<-0
STS_filtered$Previous_myocardial_infarction[STS_filtered$Previous_myocardial_infarction=='Unknown']<-0


```


# Processing Outcomes

```{r}

#We remove Oth_AFib since it is too big compared to other outcomes hence our model would only be predicting it among all the others outcomes composing AnyMAE

listOuts<-c("Reop_Bleeding","Infection","Stroke","Pulm_Pneumonia","Renal_Failure","Oth_Tamponade","Death")
#all Outs need to be numeric
for (name in names(STS_filtered[,listOuts])) {
  print(name)
STS_filtered[,name]<-as.integer(STS_filtered[,name])
}
STS_filtered$Stroke[is.na(STS_filtered$Stroke)]<-0

```

# Any Mayor Adverse Event Creation

```{r}
#We create an extra column in case any Mayor Adverse Event is ocuring during surgery

#Those events are:
# "Reop_Bleeding","Infection","Stroke","Pulm_Pneumonia","Renal_Failure","Oth_Tamponade"
#,"Death"


multi.fun <- function(x) {cbind(freq = table(x), percentage = round(prop.table(table(x))*100,2))}

STS_filtered['Any_MAE']<-rowSums(STS_filtered[,listOuts])

STS_filtered$Any_MAE<-ifelse(STS_filtered$Any_MAE==0,0,1)

STS_filtered['Total_MAE']<-rowSums(STS_filtered[,listOuts])

```

# New composite outcome

```{r}
STS_filtered<-STS_filtered%>%
               mutate(
               RFDS=if_else(
                 Renal_Failure == 1 
               | Death ==1
               | Stroke ==1,1,0)
               ,RFD=if_else(
                 Renal_Failure == 1 
               | Death ==1,1,0)
               ,DS=if_else(
                 Death ==1
               | Stroke ==1,1,0)
               ,RFS=if_else(
                 Renal_Failure == 1 
               | Stroke ==1,1,0)
               )
```


# initial tests

```{r}
multi.fun <- function(x) {cbind(freq = table(x), percentage = round(prop.table(table(x))*100,2))}

for (name in listVars){
  print(name)
print(multi.fun(STS_filtered[, name]))
}

# Check if there is any emtpy column for a certain year
for (name in names(STS_filtered[,c(listOuts)])) {
  for (year in 2008:2016){
    filtereddata<-subset(STS_filtered, format(as.Date(Surgery_Date),"%Y")==year)
  cat('\n')
  cat(year)
  cat('\n')
  cat(name)
  print(multi.fun(filtereddata[name]))
# write(name,file="printingMissingDataColumns.txt",append=TRUE)
# write(year,file="printingMissingDataColumns.txt",append=TRUE)
# write("\n",file="printingMissingDataColumns.txt",append=TRUE)
# write.table(tablesummary,file="printingMissingDataColumns.txt",append=TRUE,sep = "\t",quote = FALSE, row.names = FALSE)
      }
  
    }


  for (year in 2008:2016){
    filtereddata<-subset(STS_filtered, format(as.Date(Surgery_Date),"%Y")==year)
    cat('\n')
    cat(year)
    cat('\n')
    print(multi.fun(filtereddata$Infection ))
  }

for (name in names(STS_filtered[,c(listVars)])) {
  cat('\n')
  cat(name)
  print(multi.fun(STS_filtered[name]))
  print(summary(STS_filtered[name]))
# write(name,file="printingMissingDataColumns.txt",append=TRUE)
# write(year,file="printingMissingDataColumns.txt",append=TRUE)
# write("\n",file="printingMissingDataColumns.txt",append=TRUE)
# write.table(tablesummary,file="printingMissingDataColumns.txt",append=TRUE,sep = "\t",quote = FALSE, row.names = FALSE)
      }
  

```

