---
title: "7_HPE_Study_AUT_AWI_and_ratios"
author: "Miguel Angel Armengol de la Hoz"
output:
  html_document:
    toc: true
    theme: united
---
# Load the enviroment and data

```{r}

#load("C:/BIG FILES/Phenotyping/HemodynamicProjectsDatasetFeb18.RData")

#load libs
library(dplyr)
library(xlsx)
library(compare)
```

# Hypothension episodes location dataset

We need a dataset to know in which period of the surgery (preCPB|CPB|postCPB) our timestamps are taking place.

```{r eval=FALSE, include=FALSE}
All_Cases<-data.frame(unique(VitalsignsF$Case_Name))
colnames(All_Cases)[1]<-'Case_Name'

VitalsignsandCPBTimes <- merge(VitalsignsF, rCPBEventsDF, by = c('Case_Name'), all = FALSE)
#In fVitalsignsDF index is useless and we need to order by Case_Name and Time!
VitalsignsandCPBTimes<-VitalsignsandCPBTimes%>%
arrange(Case_Name, Time)

#here we identify in which period of the CPB our timestamp is taking place
VitalsignsandCPBTimes<-VitalsignsandCPBTimes %>% mutate(preCPB= if_else(Time<CPB_Begin_Time,1,0))
VitalsignsandCPBTimes<-VitalsignsandCPBTimes %>% mutate(CPB= if_else(Time>=CPB_Begin_Time & Time<=CPB_End_Time,1,0))
VitalsignsandCPBTimes<-VitalsignsandCPBTimes %>% mutate(postCPB= if_else(Time>CPB_End_Time,1,0))

```

# MAP

- AWI: Area within the interval.
- AUT: Area under the threshold.
- AOT: Area over the threshold.

## AUT MAP <= 50 mmHg length per period and ratios


```{r}


#Solving select problem!!!!!!:

#select causes problem since it is also in package MASS
#use dplyr::select( to solve it


#AUT50MAP_total_min calculation

#detach(package:plyr)

#detach("package:plyr", unload=TRUE) 

AUT50MAP<-VitalsignsF%>%
dplyr::select(Case_Name, MAP)%>%
group_by(Case_Name)%>%
dplyr::filter(MAP<=50)%>%
dplyr::summarise(AUT50MAP_total_min = n()*15/60)
AUT50MAP<-left_join(All_Cases, AUT50MAP)
AUT50MAP[is.na(AUT50MAP)]<-0

#AUT50MAP_total_min calculation


AUT50MAP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & MAP <=50) %>% dplyr::summarise(AUT50MAP_preCPB_min = n()*15/60)

AUT50MAP_CPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>%dplyr::filter(CPB==1 & MAP <=50) %>% dplyr::summarise(AUT50MAP_CPB_min = n()*15/60)

AUT50MAP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & MAP <=50) %>% dplyr::summarise(AUT50MAP_postCPB_min = n()*15/60)

require(plyr)
AUT50MAP<-join_all(list(AUT50MAP,AUT50MAP_preCPB,AUT50MAP_CPB,AUT50MAP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AUT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodsDF,AUT50MAP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AUT50MAP_total_ratio=round(AUT50MAP_total_min/duration_Surgery_min,2),
       AUT50MAP_preCPB_ratio=round(AUT50MAP_preCPB_min/duration_preCPB_min,2),
       AUT50MAP_CPB_ratio=round(AUT50MAP_CPB_min/duration_CPB_min,2),
       AUT50MAP_postCPB_ratio=round(AUT50MAP_postCPB_min/duration_postCPB_min,2)
       )
```

##AWI MAP >= 51 <=60 mmHg length per period and ratios

```{r}

#AUT50MAP_total_min calculation

detach(package:plyr)
AWI51_60MAP<-VitalsignsF%>%
dplyr::select(Case_Name, MAP)%>%
group_by(Case_Name)%>%
filter(MAP >= 51 & MAP <=60 ) %>%
summarise(AWI51_60MAP_total_min = n()*15/60)
AWI51_60MAP<-left_join(All_Cases, AWI51_60MAP)
AWI51_60MAP[is.na(AWI51_60MAP)]<-0

#AUT50MAP_total_min calculation
library(compare)

AWI51_60MAP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & MAP >= 51 & MAP <=60 ) %>% dplyr::summarise(AWI51_60MAP_preCPB_min = n()*15/60)

AWI51_60MAP_CPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>%dplyr::filter(CPB==1 & MAP >= 51 & MAP <=60 ) %>% dplyr::summarise(AWI51_60MAP_CPB_min = n()*15/60)

AWI51_60MAP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & MAP >= 51 & MAP <=60 ) %>% dplyr::summarise(AWI51_60MAP_postCPB_min = n()*15/60)

require(plyr)
AWI51_60MAP<-join_all(list(AWI51_60MAP,AWI51_60MAP_preCPB,AWI51_60MAP_CPB,AWI51_60MAP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AUT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodswith_AUT_AOT_and_AWI_DF,AWI51_60MAP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AWI51_60MAP_total_ratio=round(AWI51_60MAP_total_min/duration_Surgery_min,2),
       AWI51_60MAP_preCPB_ratio=round(AWI51_60MAP_preCPB_min/duration_preCPB_min,2),
       AWI51_60MAP_CPB_ratio=round(AWI51_60MAP_CPB_min/duration_CPB_min,2),
       AWI51_60MAP_postCPB_ratio=round(AWI51_60MAP_postCPB_min/duration_postCPB_min,2)
       )
```

## AWI MAP >= 61 <65 mmHg length per period and ratios

```{r}

#AUT50MAP_total_min calculation

detach(package:plyr)
AWI61_65MAP<-VitalsignsF%>%
dplyr::select(Case_Name, MAP)%>%
group_by(Case_Name)%>%
filter(MAP >= 61 & MAP <65 ) %>%
summarise(AWI61_65MAP_total_min = n()*15/60)
AWI61_65MAP<-left_join(All_Cases, AWI61_65MAP)
AWI61_65MAP[is.na(AWI61_65MAP)]<-0

#AUT50MAP_total_min calculation
library(compare)

AWI61_65MAP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & MAP >= 61 & MAP <65 ) %>% dplyr::summarise(AWI61_65MAP_preCPB_min = n()*15/60)

AWI61_65MAP_CPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>%dplyr::filter(CPB==1 & MAP >= 61 & MAP <65 ) %>% dplyr::summarise(AWI61_65MAP_CPB_min = n()*15/60)

AWI61_65MAP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & MAP >= 61 & MAP <65 ) %>% dplyr::summarise(AWI61_65MAP_postCPB_min = n()*15/60)

require(plyr)
AWI61_65MAP<-join_all(list(AWI61_65MAP,AWI61_65MAP_preCPB,AWI61_65MAP_CPB,AWI61_65MAP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AUT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodswith_AUT_AOT_and_AWI_DF,AWI61_65MAP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AWI61_65MAP_total_ratio=round(AWI61_65MAP_total_min/duration_Surgery_min,2),
       AWI61_65MAP_preCPB_ratio=round(AWI61_65MAP_preCPB_min/duration_preCPB_min,2),
       AWI61_65MAP_CPB_ratio=round(AWI61_65MAP_CPB_min/duration_CPB_min,2),
       AWI61_65MAP_postCPB_ratio=round(AWI61_65MAP_postCPB_min/duration_postCPB_min,2)
       )
```

## AOT MAP >= 65 mmHg length per period and ratios

```{r}

#AOT65MAP_total_min calculation

detach(package:plyr)
AOT65MAP<-VitalsignsF%>%
dplyr::select(Case_Name, MAP)%>%
group_by(Case_Name)%>%
filter(MAP >=65) %>%
summarise(AOT65MAP_total_min = n()*15/60)
AOT65MAP<-left_join(All_Cases, AOT65MAP)
AOT65MAP[is.na(AOT65MAP)]<-0


#AOT65MAP_total_min calculation
library(compare)

AOT65MAP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & MAP >=65) %>% dplyr::summarise(AOT65MAP_preCPB_min = n()*15/60)

AOT65MAP_CPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>%dplyr::filter(CPB==1 & MAP >=65) %>% dplyr::summarise(AOT65MAP_CPB_min = n()*15/60)

AOT65MAP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & MAP >=65) %>% dplyr::summarise(AOT65MAP_postCPB_min = n()*15/60)

require(plyr)
AOT65MAP<-join_all(list(AOT65MAP,AOT65MAP_preCPB,AOT65MAP_CPB,AOT65MAP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AUT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodswith_AUT_AOT_and_AWI_DF,AOT65MAP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AOT65MAP_total_ratio=round(AOT65MAP_total_min/duration_Surgery_min,2),
       AOT65MAP_preCPB_ratio=round(AOT65MAP_preCPB_min/duration_preCPB_min,2),
       AOT65MAP_CPB_ratio=round(AOT65MAP_CPB_min/duration_CPB_min,2),
       AOT65MAP_postCPB_ratio=round(AOT65MAP_postCPB_min/duration_postCPB_min,2)
       )
```

## AUT MAP < 65 mmHg length per period and ratios

```{r}

#AUT65MAP_total_min calculation
detach("package:plyr")
AUT65MAP<-VitalsignsF%>%
dplyr::select(Case_Name, MAP)%>%
group_by(Case_Name)%>%
filter(MAP <65) %>%
summarise(AUT65MAP_total_min = n()*15/60)
AUT65MAP<-left_join(All_Cases, AUT65MAP)
AUT65MAP[is.na(AUT65MAP)]<-0


#AUT65MAP_total_min calculation
library(compare)

AUT65MAP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & MAP <65) %>% dplyr::summarise(AUT65MAP_preCPB_min = n()*15/60)

AUT65MAP_CPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>%dplyr::filter(CPB==1 & MAP <65) %>% dplyr::summarise(AUT65MAP_CPB_min = n()*15/60)

AUT65MAP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & MAP <65) %>% dplyr::summarise(AUT65MAP_postCPB_min = n()*15/60)

require(plyr)
AUT65MAP<-join_all(list(AUT65MAP,AUT65MAP_preCPB,AUT65MAP_CPB,AUT65MAP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AUT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodswith_AUT_AOT_and_AWI_DF,AUT65MAP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AUT65MAP_total_ratio=round(AUT65MAP_total_min/duration_Surgery_min,2),
       AUT65MAP_preCPB_ratio=round(AUT65MAP_preCPB_min/duration_preCPB_min,2),
       AUT65MAP_CPB_ratio=round(AUT65MAP_CPB_min/duration_CPB_min,2),
       AUT65MAP_postCPB_ratio=round(AUT65MAP_postCPB_min/duration_postCPB_min,2)
       )
```

# SBP

## AUT SBP <= 80 mmHg length per period and ratios

```{r}

#AUT80SBP_total_min calculation

#detach(package:plyr)
AUT80SBP<-VitalsignsF%>%
dplyr::select(Case_Name, SBP)%>%
group_by(Case_Name)%>%
filter(SBP <=80) %>%
dplyr::summarise(AUT80SBP_total_min = n()*15/60)
AUT80SBP<-left_join(All_Cases, AUT80SBP)
AUT80SBP[is.na(AUT80SBP)]<-0


#AUT80SBP_total preCPB and postCPB min calculation
library(compare)

AUT80SBP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & SBP <=80) %>%  dplyr::summarise(AUT80SBP_preCPB_min = n()*15/60)

AUT80SBP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & SBP <=80) %>% dplyr::summarise(AUT80SBP_postCPB_min = n()*15/60)

require(plyr)
AUT80SBP<-join_all(list(AUT80SBP,AUT80SBP_preCPB,AUT80SBP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AUT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodswith_AUT_AOT_and_AWI_DF,AUT80SBP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AUT80SBP_total_ratio=round(AUT80SBP_total_min/duration_Surgery_min,2),
       AUT80SBP_preCPB_ratio=round(AUT80SBP_preCPB_min/duration_preCPB_min,2),
       AUT80SBP_postCPB_ratio=round(AUT80SBP_postCPB_min/duration_postCPB_min,2)
       )
```

## AOT SBP >80 mmHg length per period and ratios

```{r}

#AOT80SBP_total_min calculation

detach(package:plyr)
AOT80SBP<-VitalsignsF%>%
dplyr::select(Case_Name, SBP)%>%
group_by(Case_Name)%>%
filter(SBP >80) %>%
dplyr::summarise(AOT80SBP_total_min = n()*15/60)
AOT80SBP<-left_join(All_Cases, AOT80SBP)
AOT80SBP[is.na(AOT80SBP)]<-0

#AOT80SBP_total preCPB and postCPB min calculation
library(compare)

AOT80SBP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & SBP >80) %>%  dplyr::summarise(AOT80SBP_preCPB_min = n()*15/60)

AOT80SBP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & SBP >80) %>%  dplyr::summarise(AOT80SBP_postCPB_min = n()*15/60)

require(plyr)
AOT80SBP<-join_all(list(AOT80SBP,AOT80SBP_preCPB,AOT80SBP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AOT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodswith_AUT_AOT_and_AWI_DF,AOT80SBP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AOT80SBP_total_ratio=round(AOT80SBP_total_min/duration_Surgery_min,2),
       AOT80SBP_preCPB_ratio=round(AOT80SBP_preCPB_min/duration_preCPB_min,2),
       AOT80SBP_postCPB_ratio=round(AOT80SBP_postCPB_min/duration_postCPB_min,2)
       )
```

# DBP

## AUT DBP <= 30 mmHg length per period and ratios

```{r}

#AUT30DBP_total_min calculation

detach(package:plyr)
AUT30DBP<-VitalsignsF%>%
dplyr::select(Case_Name, DBP)%>%
group_by(Case_Name)%>%
filter(DBP <=30) %>%
summarise(AUT30DBP_total_min = n()*15/60)
AUT30DBP<-left_join(All_Cases, AUT30DBP)
AUT30DBP[is.na(AUT30DBP)]<-0

#AUT30DBP_total preCPB and postCPB min calculation
library(compare)

AUT30DBP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & DBP <=30) %>% dplyr::summarise(AUT30DBP_preCPB_min = n()*15/60)

AUT30DBP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & DBP <=30) %>% dplyr::summarise(AUT30DBP_postCPB_min = n()*15/60)

require(plyr)
AUT30DBP<-join_all(list(AUT30DBP,AUT30DBP_preCPB,AUT30DBP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AUT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodswith_AUT_AOT_and_AWI_DF,AUT30DBP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AUT30DBP_total_ratio=round(AUT30DBP_total_min/duration_Surgery_min,2),
       AUT30DBP_preCPB_ratio=round(AUT30DBP_preCPB_min/duration_preCPB_min,2),
       AUT30DBP_postCPB_ratio=round(AUT30DBP_postCPB_min/duration_postCPB_min,2)
       )
```

## AOT DBP > 30 mmHg length per period and ratios

```{r}

#AOT30DBP_total_min calculation

detach(package:plyr)
AOT30DBP<-VitalsignsF%>%
dplyr::select(Case_Name, DBP)%>%
group_by(Case_Name)%>%
filter(DBP >30) %>%
summarise(AOT30DBP_total_min = n()*15/60)
AOT30DBP<-left_join(All_Cases, AOT30DBP)
AOT30DBP[is.na(AOT30DBP)]<-0

#AOT30DBP_total preCPB and postCPB min calculation
library(compare)

AOT30DBP_preCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(preCPB==1 & DBP >30) %>% dplyr::summarise(AOT30DBP_preCPB_min = n()*15/60)

AOT30DBP_postCPB<-VitalsignsandCPBTimes %>% dplyr::group_by(Case_Name) %>% dplyr::filter(postCPB==1 & DBP >30) %>% dplyr::summarise(AOT30DBP_postCPB_min = n()*15/60)

require(plyr)
AOT30DBP<-join_all(list(AOT30DBP,AOT30DBP_preCPB,AOT30DBP_postCPB), by ='Case_Name')

#now we add the ratios, for that we need duration info thus we merge our AOT dataset with AllPeriodsDF

AllPeriodswith_AUT_AOT_and_AWI_DF<-left_join(AllPeriodswith_AUT_AOT_and_AWI_DF,AOT30DBP)

AllPeriodswith_AUT_AOT_and_AWI_DF<-AllPeriodswith_AUT_AOT_and_AWI_DF%>%
mutate(AOT30DBP_total_ratio=round(AOT30DBP_total_min/duration_Surgery_min,2),
       AOT30DBP_preCPB_ratio=round(AOT30DBP_preCPB_min/duration_preCPB_min,2),
       AOT30DBP_postCPB_ratio=round(AOT30DBP_postCPB_min/duration_postCPB_min,2)
       )
```

# New AUC-related Variables

## MAP

### AUC MAP < 65 Variable Creation

AUC under 65 mmHg Dataset creation

```{r}

detach("package:plyr")
AUC65MAP<-VitalsignsF%>%
dplyr::select(Case_Name, MAP)%>%
filter(MAP<65) %>%
mutate(rectangle=(65-MAP)*0.25) %>%
group_by(Case_Name)%>%
summarise(AUC65MAP_total_mmHgmin = sum(rectangle)) %>%
arrange(Case_Name)

AUC65MAP_CPB<-VitalsignsandCPBTimes %>%
dplyr::group_by(Case_Name) %>%
dplyr::filter(CPB==1 & MAP <65) %>%
mutate(rectangle=(65-MAP)*0.25) %>%
group_by(Case_Name)%>%
summarise(AUC65MAP_CPB_total_mmHgmin = sum(rectangle)) %>%
arrange(Case_Name)

```

### AOC MAP > 65 Variable Creation

AOC over or equal 65 mmHg Dataset creation

```{r}

#detach("package:plyr")

AOC65MAP<-VitalsignsF%>%
dplyr::select(Case_Name, MAP)%>%
filter(MAP >=65) %>%
mutate(rectangle=(MAP-65)*0.25) %>%
group_by(Case_Name)%>%
summarise(AOC65MAP_total_mmHgmin = sum(rectangle)) %>%
arrange(Case_Name)
```

### Combined TWA & AUC MAP <= 65 and All_AUC65MAP_variables Variable Creation

TWA-MAP under 65 mmHg dataset creation

```{r}
require(dplyr)
All_AUC65MAP_variables<-left_join(AllPeriodsDF,AUC65MAP)%>%
dplyr::select(Case_Name, duration_Surgery_min,AUC65MAP_total_mmHgmin)%>%
mutate(TWA65MAP_total_mmHg=round(AUC65MAP_total_mmHgmin/duration_Surgery_min,2)) %>%
dplyr::select(Case_Name,AUC65MAP_total_mmHgmin,TWA65MAP_total_mmHg)

All_AUC65MAP_variables<-left_join(All_AUC65MAP_variables,AUC65MAP_CPB)
#In case we want to add  TWA:
# dplyr::select(Case_Name, duration_Surgery_min,AUC65MAP_CPB_total_mmHgmin)%>%
#   mutate(TWA65MAP_total_mmHg=round(AUC65MAP_total_mmHgmin/duration_Surgery_min,2)) %>%
#   select(Case_Name,AUC65MAP_total_mmHgmin,TWA65MAP_total_mmHg)

All_AUC65MAP_variables<-left_join(All_AUC65MAP_variables, AOC65MAP)
# those that didn't have values <65 or >=65 spent 0 minutes in the threshold.
All_AUC65MAP_variables[is.na(All_AUC65MAP_variables)]<-0

```

# REPLACING NA with 0

## Replacing 0 in CPB related calculated colums

What to do for those CPB-related variables that have no CPB times? 
_We exclude those cases_

```{r eval=FALSE, include=FALSE}

#nested if else function creation

i <- function(if_stat, then) {
  if_stat <- lazyeval::expr_text(if_stat)
  then    <- lazyeval::expr_text(then)
  sprintf("ifelse(%s, %s, ", if_stat, then)
}

e <- function(else_ret) {
  else_ret <- lazyeval::expr_text(else_ret)
  else_ret
}

ie <- function(...) {
  args <- list(...)
  
  for (i in 1:(length(args) - 1) ) {
      if (substr(args[[i]], 1, 6) != "ifelse") {
        stop("All but the last argument, need to be i functions.", call. = FALSE)
      }
  }
  if (substr(args[[length(args)]], 1, 6) == "ifelse"){
    stop("Last argument needs to be an e function.", call. = FALSE)
  }
  args$final <- paste(rep(')', length(args) - 1), collapse = '')
  eval_string <- do.call('paste', args)
  eval(parse(text = eval_string))
}



preCPBcols<-names(AllPeriodswith_AUT_AOT_and_AWI_DF[,grep('preCPB_ratio|preCPB_min', names(AllPeriodswith_AUT_AOT_and_AWI_DF))])
for (n in 1:length(CPBcols)) {
  colnam<-CPBcols[n]
#print(AllPeriodswith_AUT_AOT_and_AWI_DF[,colnam] )
AllPeriodswith_AUT_AOT_and_AWI_DF[,colnam] <- 
#    i( is.na(AllPeriodswith_AUT_AOT_and_AWI_DF[,colnam])  ,   NA),
    ie(
    i(  is.na(AllPeriodswith_AUT_AOT_and_AWI_DF$Sur_Begin_Time) ,   1),
    i(  is.na(AllPeriodswith_AUT_AOT_and_AWI_DF$CPB_Begin_Time) ,   2),
    e(0)
  )

i(if_stat = 3>4,2)

}


```

## checking durations with neg values

```{r eval=FALSE, include=FALSE}
durations<-names(FinalHemodynamicsDataset[,grep('_min', names(FinalHemodynamicsDataset))])
for (i in 1:length(durations)) {
  colnam<-durations[i]
  if(sum(FinalHemodynamicsDataset[,colnam] <0, na.rm = TRUE)>0){
      cat(colnam)
   print(sum(FinalHemodynamicsDataset[,colnam] <0, na.rm = TRUE))
  }
}
```


```{r eval=FALSE, include=FALSE}
STS_filtered$Stroke[is.na(STS_filtered$AUT50MAP_total_min)]<-0
```

