---
title: "Anesthesiologists Selection, Surgeons_all_yearsDF, Any MAE"
author: "Miguel Ángel Armengol de la Hoz"
date: "10 de agosto de 2017"
output: 
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#load the data
library(dplyr)
#load("C:/BIG FILES/Phenotyping/HemodynamicProjectsDatasetFeb18.RData")
```

#Providers dataframes 

##Cleaning Providers dataframe (ComboDF creation)

```{r}
ComboDF<- rbind(Combo08, Combo09, Combo10,Combo11,Combo12,Combo13,Combo14,Combo15,Combo16)

#Correcting the mistake in duplicate physician Correct Name:Qi Ott, MD
ComboDF$C_Item[ComboDF$C_Item==21342]<-21619
# Combo09$C_Item[Combo09$C_Item==21342]<-21619
# Combo10$C_Item[Combo10$C_Item==21342]<-21619
# Combo11$C_Item[Combo11$C_Item==21342]<-21619
# Combo12$C_Item[Combo12$C_Item==21342]<-21619
# Combo13$C_Item[Combo13$C_Item==21342]<-21619
# Combo14$C_Item[Combo14$C_Item==21342]<-21619
# Combo15$C_Item[Combo15$C_Item==21342]<-21619
# Combo16$C_Item[Combo16$C_Item==21342]<-21619

#Correcting the mistake in duplicate physician Correct Name:Qi Ott, MD
ComboDF$C_Item[ComboDF$C_Item==21342]<-21619

ComboDF$Time<-NULL
ComboDF$ItemID<-NULL
ComboDF$C_Type<-NULL
ComboDF$C_Type_Label<-NULL
ComboDF$C_Association<-NULL
ComboDF$ComboText<-NULL
ComboDF$ESIG<-NULL
ComboDF$ESIGNAMETEXT<-NULL
ComboDF$ESIGDATEANDTIME<-NULL

```

## Selected Anesthesiologists DF

In this list we select Anesthesiologists performing overall >=30 surgeries from 2008-2016

```{r}
#Selecting anesthesiologists
library(dplyr)
Anesthesiologists_selection<-subset(ComboDF, ComboDF$C_Item %in% c(20025,20026,20030,20036,20038,20051,20156,20359,20556,20935,21084,21105,21379,21507,21619,21839)
                                    & Label== 'Attending Anesthesiologist')

unique(Anesthesiologists_selection)

Anesthesiologists_selection<-Anesthesiologists_selection %>%
mutate(Anesthesiologist=C_Item) %>%
dplyr::select(Case_Name,Anesthesiologist)

Anesthesiologists_selection<-unique(Anesthesiologists_selection)

```

## Selected Surgeons DF

This code needs to be rewriten in case we want to select surgeons under a different criteria. The list of surgeons below was selected by including only those who were performing surgery every year.

```{r eval=FALSE, include=FALSE}
#Selecting surgeons

#Focus only on these 3 Surgeons
library(dplyr)
Surgeons_all_yearsDF<-subset(ComboDF, ComboDF$C_Item %in% c(20306,20479,20966))

Surgeons_all_yearsDF<-Surgeons_all_yearsDF %>%
mutate(Surgeon=C_Item) %>%
 dplyr::select(Case_Name,Surgeon)
```


 1  20036 Peter J. Panzica, MD        
 2  20306 Khabbaz, Kamal M.D.         
 3  20306 Khabbaz, Kamal M.D.         
 4  20036 Peter J. Panzica, MD        
 5  20036 Peter J. Panzica, MD        
 6  20026 Adam B. Lerner, MD          
 7  20556 Balachundhar Subramaniam, MD
 8  20026 Adam B. Lerner, MD          
 9  20026 Adam B. Lerner, MD          
10  20030 Feroze Mahmood, MD  

<!-- # Coefficient of variation, as percent -->
<!-- ```{r, eval=FALSE, include=FALSE, null_prefix=TRUE} -->
<!-- library(dplyr) -->

<!-- anesthesiologists<-unique(sort(Ljoin_AnestPlots$C_Item)) -->

<!-- anesthesiologist<-20025 -->
<!-- print(paste('Coefficient of variation, as percent for anesthesiologist:',anesthesiologist)) -->
<!--   for(year in 2008:2016){ -->
<!-- subset<-filter(FinalHemodynamicsDataset, format(as.Date(FinalHemodynamicsDataset$Surgery_Date),"%Y")==year & FinalHemodynamicsDataset$Anesthesiologist==anesthesiologist) -->
<!-- print(paste('Year:',year)) -->
<!-- print(sd(subset$, na.rm=TRUE)/ mean(subset$AUC60MAP_SL_ratio, na.rm=TRUE)*100) -->
<!--   } -->

<!-- anesthesiologist<-20026 -->
<!-- print(paste('Coefficient of variation, as percent for anesthesiologist:',anesthesiologist)) -->
<!--   for(year in 2008:2016){ -->
<!-- subset<-filter(Ljoin_AnestPlots, format(as.Date(Ljoin_AnestPlots$Surgery_Date),"%Y")==year & Ljoin_AnestPlots$C_Item==anesthesiologist) -->
<!-- print(paste('Year:',year)) -->
<!-- print(sd(subset$AUC60MAP_SL_ratio, na.rm=TRUE)/ mean(subset$AUC60MAP_SL_ratio, na.rm=TRUE)*100) -->
<!--   } -->

<!-- anesthesiologist<-20030 -->
<!-- print(paste('Coefficient of variation, as percent for anesthesiologist:',anesthesiologist)) -->
<!--   for(year in 2008:2016){ -->
<!-- subset<-filter(Ljoin_AnestPlots, format(as.Date(Ljoin_AnestPlots$Surgery_Date),"%Y")==year & Ljoin_AnestPlots$C_Item==anesthesiologist) -->
<!-- print(paste('Year:',year)) -->
<!-- print(sd(subset$AUC60MAP_SL_ratio, na.rm=TRUE)/ mean(subset$AUC60MAP_SL_ratio, na.rm=TRUE)*100) -->
<!--   } -->

<!-- anesthesiologist<-20036 -->
<!-- print(paste('Coefficient of variation, as percent for anesthesiologist:',anesthesiologist)) -->
<!--   for(year in 2008:2016){ -->
<!-- subset<-filter(Ljoin_AnestPlots, format(as.Date(Ljoin_AnestPlots$Surgery_Date),"%Y")==year & Ljoin_AnestPlots$C_Item==anesthesiologist) -->
<!-- print(paste('Year:',year)) -->
<!-- print(sd(subset$AUC60MAP_SL_ratio, na.rm=TRUE)/ mean(subset$AUC60MAP_SL_ratio, na.rm=TRUE)*100) -->
<!--   } -->

<!-- anesthesiologist<-20051 -->
<!-- print(paste('Coefficient of variation, as percent for anesthesiologist:',anesthesiologist)) -->
<!--   for(year in 2008:2016){ -->
<!-- subset<-filter(Ljoin_AnestPlots, format(as.Date(Ljoin_AnestPlots$Surgery_Date),"%Y")==year & Ljoin_AnestPlots$C_Item==anesthesiologist) -->
<!-- print(paste('Year:',year)) -->
<!-- print(sd(subset$AUC60MAP_SL_ratio, na.rm=TRUE)/ mean(subset$AUC60MAP_SL_ratio, na.rm=TRUE)*100) -->
<!--   } -->

<!-- anesthesiologist<-20359 -->
<!-- print(paste('Coefficient of variation, as percent for anesthesiologist:',anesthesiologist)) -->
<!--   for(year in 2008:2016){ -->
<!-- subset<-filter(Ljoin_AnestPlots, format(as.Date(Ljoin_AnestPlots$Surgery_Date),"%Y")==year & Ljoin_AnestPlots$C_Item==anesthesiologist) -->
<!-- print(paste('Year:',year)) -->
<!-- print(sd(subset$AUC60MAP_SL_ratio, na.rm=TRUE)/ mean(subset$AUC60MAP_SL_ratio, na.rm=TRUE)*100) -->
<!--   } -->

<!-- anesthesiologist<-20556 -->
<!-- print(paste('Coefficient of variation, as percent for anesthesiologist:',anesthesiologist)) -->
<!--   for(year in 2008:2016){ -->
<!-- subset<-filter(Ljoin_AnestPlots, format(as.Date(Ljoin_AnestPlots$Surgery_Date),"%Y")==year & Ljoin_AnestPlots$C_Item==anesthesiologist) -->
<!-- print(paste('Year:',year)) -->
<!-- print(sd(subset$AUC60MAP_SL_ratio, na.rm=TRUE)/ mean(subset$AUC60MAP_SL_ratio, na.rm=TRUE)*100) -->
<!--   } -->
<!-- ``` -->


<!-- ## Finding providers appearing all years -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- appearance_08<-data.frame(C_Item=unique(sort(Combo08$C_Item))) -->
<!-- appearance_08['appearing08']<-1 -->
<!-- appearance_09<-data.frame(C_Item=unique(sort(Combo09$C_Item))) -->
<!-- appearance_09['appearing09']<-1 -->
<!-- appearance_10<-data.frame(C_Item=unique(sort(Combo10$C_Item))) -->
<!-- appearance_10['appearing10']<-1 -->
<!-- appearance_11<-data.frame(C_Item=unique(sort(Combo11$C_Item))) -->
<!-- appearance_11['appearing11']<-1 -->
<!-- appearance_12<-data.frame(C_Item=unique(sort(Combo12$C_Item))) -->
<!-- appearance_12['appearing12']<-1 -->
<!-- appearance_13<-data.frame(C_Item=unique(sort(Combo13$C_Item))) -->
<!-- appearance_13['appearing13']<-1 -->
<!-- appearance_14<-data.frame(C_Item=unique(sort(Combo14$C_Item))) -->
<!-- appearance_14['appearing14']<-1 -->
<!-- appearance_15<-data.frame(C_Item=unique(sort(Combo15$C_Item))) -->
<!-- appearance_15['appearing15']<-1 -->
<!-- appearance_16<-data.frame(C_Item=unique(sort(Combo16$C_Item))) -->
<!-- appearance_16['appearing16']<-1 -->

<!-- citemlists<-left_join(data.frame(C_Item=unique(sort(ComboDF$C_Item))), appearance_08) -->
<!-- citemlists<-left_join(citemlists, appearance_09) -->
<!-- citemlists<-left_join(citemlists, appearance_10) -->
<!-- citemlists<-left_join(citemlists, appearance_11) -->
<!-- citemlists<-left_join(citemlists, appearance_12) -->
<!-- citemlists<-left_join(citemlists, appearance_13) -->
<!-- citemlists<-left_join(citemlists, appearance_14) -->
<!-- citemlists<-left_join(citemlists, appearance_15) -->
<!-- citemlists<-left_join(citemlists, appearance_16) -->
<!-- citemlists[is.na(citemlists)]<-0 -->

<!-- #creating an extra column with providers appearing all years -->
<!-- library(dplyr) -->
<!-- citemlists<-citemlists %>% -->
<!-- mutate(appearingallyears=if_else(rowSums(citemlists[,-1])==9,1,0)) -->
<!-- ``` -->


