---
title: "Vasopressors Columns Creation"
author: "Miguel Angel Armengol de la Hoz"
date: "10 de agosto de 2017"
output: 
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#load the data
library(dplyr)
#load("~/BIG FILES/Phenotyping/HemodynamicProjectsDatasetFeb18.RData")
```


# Using the new Drugs total table


DRUGTEXT

-Excluded:
 Calcium Chloride
 Calcium Gluconate
 Methylene Blue (Only 43 cases)


-Group A:
Phenylephrine
Ephedrine
Norepinephrine
Vasopressin
Norepinephrine (800/50)

-Group B
Milrinone
Epinephrine


## Load data and convert units

```{r}
library(readr)
library(readxl)
DrugTotals_forstudy <- read_csv("~/BIG FILES/Phenotyping/DrugTotals_forstudy.csv", 
    col_types = readr::cols(DOS = col_date(format = "%m/%d/%Y"), 
        Group = readr::col_factor(levels = c("A","B"))))

#DrugTotals_forstudy<-
#detach(package:plyr)
DrugTotals_forstudy<-DrugTotals_forstudy %>% 
mutate(converted_dose_mg=if_else(UNITOFMEASURETEXT=="mcg", round(DOSEAMOUNT/1000,2),round(DOSEAMOUNT,2)))

#remove rows without drug info
DrugTotals_forstudy<-DrugTotals_forstudy[!is.na(DrugTotals_forstudy$DRUGTEXT),]
```



# Drugs with formula

generate vasopressors = epinephrinetotal + norepinephrinetotal + (phenylephrinetotal / 10) + (dopaminetotal / weightkg / 2)

*Final used Formula*
generate vasopressors = epinephrinetotal + norepinephrinetotal + (phenylephrinetotal / 10) + (milrinonetotal/5) + (vasopressin * 8.33)

(milrinone equivalence added by clinical criteria)

Ref: Mancl, E. E., & Muzevich, K. M. (2013). Tolerability and safety of enteral nutrition in critically ill patients receiving intravenous vasopressor therapy. Journal of parenteral and enteral nutrition, 37(5), 641-651.

```{r}
drugsinformula<-subset(DrugTotals_forstudy, DrugTotals_forstudy$DRUGTEXT %in% c("Phenylephrine",    "Epinephrine","Norepinephrine","Norepinephrine (800/50)","Milrinone","Vasopressin") )

drugsinformula$DRUGTEXT[drugsinformula$DRUGTEXT=='Norepinephrine (800/50)']<-"Norepinephrine"
drugsinformula$MRN<-NULL
drugsinformula$DOS<-NULL                         
drugsinformula$Vasopressor<-NULL
drugsinformula$DRUGITEMID<-NULL
drugsinformula$EZINDEX<-NULL
drugsinformula$CONTAINERTEXT<-NULL

drugsinformula<-drugsinformula %>% 
  mutate(converted_dose_mg=if_else(UNITOFMEASURETEXT=="mcg", round(DOSEAMOUNT/1000,2),round(DOSEAMOUNT,2) )
  )

drugsinformula$DOSEAMOUNT<-NULL
drugsinformula$UNITOFMEASURETEXT<-NULL

library(dplyr)
drugsinformula<-drugsinformula %>%
dplyr::group_by(CASENUMBER, DRUGTEXT) %>%
dplyr::summarise(total_indiv_drug=sum(converted_dose_mg))

library(data.table)

r_drugsinformula<-dcast(drugsinformula, CASENUMBER ~ DRUGTEXT, value.var='total_indiv_drug')
r_drugsinformula[is.na(r_drugsinformula)]<-0

#generate vasopressors = epinephrinetotal + norepinephrinetotal + (phenylephrinetotal / 10) + milrinonetotal/5

generate_vasopressors <- function(epinephrinetotal,norepinephrinetotal,phenylephrinetotal,milrinonetotal,vasopressintotal){
return(epinephrinetotal+norepinephrinetotal+(phenylephrinetotal/10)+(milrinonetotal/5)+
         (vasopressintotal * 8.33)
       )
}
r_drugsinformula<-r_drugsinformula%>%
  mutate(total_pressors_formula_mg=round(generate_vasopressors(Epinephrine, Norepinephrine,Phenylephrine,Milrinone,Vasopressin) ,3))
colnames(r_drugsinformula)[1]<-'Case_Name'
```








