---
title: "Vasopressors Columns Creation"
author: "Miguel Angel Armengol de la Hoz"
date: "10 de agosto de 2017"
output: 
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#load the data
library(dplyr)
#load("~/BIG FILES/Phenotyping/HemodynamicProjectsDatasetFeb18.RData")
```


#Using the new Drugs total table


DRUGTEXT

-Excluded:
 Calcium Chloride
 Calcium Gluconate
 Methylene Blue (Only 43 cases)


-Group A:
Phenylephrine
Ephedrine
Norepinephrine
Vasopressin
Norepinephrine (800/50)

-Group B
Milrinone
Epinephrine


## Load data and convert units

```{r eval=FALSE, include=FALSE}
library(readr)
library(readxl)
DrugTotals_forstudy <- read_csv("~/BIG FILES/Phenotyping/DrugTotals_forstudy.csv", 
    col_types = readr::cols(DOS = col_date(format = "%m/%d/%Y"), 
        Group = readr::col_factor(levels = c("A","B"))))

#DrugTotals_forstudy<-
#detach(package:plyr)
DrugTotals_forstudy<-DrugTotals_forstudy %>% 
mutate(converted_dose_mg=if_else(UNITOFMEASURETEXT=="mcg", round(DOSEAMOUNT/1000,2),round(DOSEAMOUNT,2)))

#remove vasopresing so we can interpretate the dosing        
#DrugTotals_forstudy<-DrugTotals_forstudy[!(DrugTotals_forstudy$DRUGTEXT=="Vasopressin"),]

#remove rows without drug info
DrugTotals_forstudy<-DrugTotals_forstudy[!is.na(DrugTotals_forstudy$DRUGTEXT),]
```



# Drugs with formula

generate vasopressors = epinephrinetotal + norepinephrinetotal + (phenylephrinetotal / 10) + (dopaminetotal / weightkg / 2)

generate vasopressors = epinephrinetotal + norepinephrinetotal + (phenylephrinetotal / 10) + (milrinonetotal/5) + (vasopressin * 8.33)

(milrinone equivalence added by clinical criteria)

Ref: Mancl, E. E., & Muzevich, K. M. (2013). Tolerability and safety of enteral nutrition in critically ill patients receiving intravenous vasopressor therapy. Journal of parenteral and enteral nutrition, 37(5), 641-651.

```{r}
drugsinformula<-subset(DrugTotals_forstudy, DrugTotals_forstudy$DRUGTEXT %in% c("Phenylephrine","Epinephrine","Norepinephrine","Norepinephrine (800/50)","Milrinone","Vasopressin") )

drugsinformula$DRUGTEXT[drugsinformula$DRUGTEXT=='Norepinephrine (800/50)']<-"Norepinephrine"
drugsinformula$MRN<-NULL
drugsinformula$DOS<-NULL                         
drugsinformula$Vasopressor<-NULL
drugsinformula$DRUGITEMID<-NULL
drugsinformula$EZINDEX<-NULL
drugsinformula$CONTAINERTEXT<-NULL

drugsinformula<-drugsinformula %>% 
  mutate(converted_dose_mg=if_else(UNITOFMEASURETEXT=="mcg", round(DOSEAMOUNT/1000,2),round(DOSEAMOUNT,2) )
  )

drugsinformula$DOSEAMOUNT<-NULL
drugsinformula$UNITOFMEASURETEXT<-NULL

library(dplyr)
drugsinformula<-drugsinformula %>%
dplyr::group_by(CASENUMBER, DRUGTEXT) %>%
dplyr::summarise(total_indiv_drug=sum(converted_dose_mg))

library(data.table)

r_drugsinformula<-dcast(drugsinformula, CASENUMBER ~ DRUGTEXT, value.var='total_indiv_drug')
r_drugsinformula[is.na(r_drugsinformula)]<-0

#generate vasopressors = epinephrinetotal + norepinephrinetotal + (phenylephrinetotal / 10) 

# + milrinonetotal/5 EXCLUDED FROM THE FORMULA (it was the last term 09202020)

# we decided to exclude milrinone per reviewer request for our September 2020 resubmission

generate_vasopressors <- function(epinephrinetotal,norepinephrinetotal,phenylephrinetotal,vasopressintotal){
return(epinephrinetotal+norepinephrinetotal+(phenylephrinetotal/10)+
         (vasopressintotal * 8.33)
       )
}
r_drugsinformula<-r_drugsinformula%>%
  mutate(
    total_pressors_formula_mg=round(generate_vasopressors(Epinephrine, Norepinephrine,Phenylephrine,Vasopressin) ,3)
    ,milrinone=Milrinone
    )
colnames(r_drugsinformula)[1]<-'Case_Name'
```


#___NOT_USED ANYMORE______

# Correcting NA

```{r}
# We are only interested on those Cases that have both Vitalsigns data and drug data
r_drugsinformula<-inner_join(All_Cases, r_drugsinformula)
r_drugsinformula[is.na(r_drugsinformula)]<-0

#The join returned 5504 thus there are 204 cases with no drug invormation. We are making all those cases NA since we have no drug info about them.
```


# OLD Bolus Drugs

## Bolus Drugs quantities

```{r eval=FALSE, include=FALSE}
library(dplyr)

BolusDrugsDF <- rbind(BolusDrugs08, BolusDrugs09, BolusDrugs10,BolusDrugs11,BolusDrugs12,BolusDrugs13,BolusDrugs14,BolusDrugs15,BolusDrugs16)

#After creating our DF, let's perform our filtering and table reshape

BolusDrugsDF<-subset(BolusDrugsDF, BolusDrugsDF$Label!= 'Calcium Chloride' & BolusDrugsDF$Label != 'Calcium Gluconate')

#BolusDrugsDF$Time<-NULL
BolusDrugsDF$ItemID<-NULL
BolusDrugsDF$Route<-NULL
BolusDrugsDF$ESIG<-NULL
BolusDrugsDF$ESIGNAMETEXT<-NULL
BolusDrugsDF$ESIGDATEANDTIME<-NULL

#unique(BolusDrugsDF$Label)

BolusDrugsDF<-BolusDrugsDF %>% mutate(Phenylephrine= if_else(Label == 'Phenylephrine',1,0))
BolusDrugsDF<-BolusDrugsDF %>% mutate(Epinephrine= if_else(Label == 'Epinephrine',1,0))
BolusDrugsDF<-BolusDrugsDF %>% mutate('Norepinephrine (800/50)'= if_else(Label == 'Norepinephrine (800/50)' ,1,0))
BolusDrugsDF<-BolusDrugsDF %>% mutate('Norepinephrine'= if_else(Label == 'Norepinephrine' ,1,0))
BolusDrugsDF<-BolusDrugsDF %>% mutate('Vasopressin'= if_else(Label == 'Vasopressin' ,1,0))




library(reshape)

bolusdrugspercase<-reshape(BolusDrugsDF, timevar = 'Label' , idvar = 'Case_Name', direction = 'wide')

#barplot(table(BolusDrugsDF$Units[BolusDrugsDF$Label=='Phenylephrine']))

```

## Bolus Drugs binary CPB location

```{r eval=FALSE, include=FALSE}
library(dplyr)

BolusDrugsDF_CPBloc<- rbind(BolusDrugs08, BolusDrugs09, BolusDrugs10,BolusDrugs11,BolusDrugs12,BolusDrugs13,BolusDrugs14,BolusDrugs15,BolusDrugs16)

#After creating our DF, let's perform our filtering and table reshape

BolusDrugsDF_CPBloc<-subset(BolusDrugsDF_CPBloc, BolusDrugsDF_CPBloc$Label!='Calcium Chloride' & BolusDrugsDF_CPBloc$Label != 'Calcium Gluconate')

#BolusDrugsDF_CPBloc$Time<-NULL
BolusDrugsDF_CPBloc$ItemID<-NULL
BolusDrugsDF_CPBloc$Route<-NULL
BolusDrugsDF_CPBloc$ESIG<-NULL
BolusDrugsDF_CPBloc$ESIGNAMETEXT<-NULL
BolusDrugsDF_CPBloc$ESIGDATEANDTIME<-NULL

#merge the datasets we need
BolusDrugsDF_CPBloc<-merge(BolusDrugsDF_CPBloc, rCPBEventsDF)

##Add the bypass begin and end for comparation

#preCPB
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Phenylephrine_preCPB = if_else(Label == 'Phenylephrine' & Time < CPB_Begin_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Epinephrine_preCPB = if_else(Label == 'Epinephrine' & Time < CPB_Begin_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Epinephrine_preCPB= if_else(Label == 'Epinephrine'& Time < CPB_Begin_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate('Norepinephrine(800/50)_preCPB'= if_else(Label == 'Norepinephrine (800/50)' & Time < CPB_Begin_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate('Norepinephrine_preCPB'= if_else(Label == 'Norepinephrine' & Time < CPB_Begin_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Vasopressin_preCPB= if_else(Label == 'Vasopressin' & Time < CPB_Begin_Time ,1,0))


#CPB
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Phenylephrine_CPB = if_else(Label == 'Phenylephrine' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Epinephrine_CPB = if_else(Label == 'Epinephrine' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Epinephrine_CPB= if_else(Label == 'Epinephrine'& Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate('Norepinephrine(800/50)_CPB'= if_else(Label == 'Norepinephrine (800/50)' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate('Norepinephrine_CPB'= if_else(Label == 'Norepinephrine' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Vasopressin_CPB= if_else(Label == 'Vasopressin' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))


#postCPB
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Phenylephrine_postCPB = if_else(Label == 'Phenylephrine' & Time > CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Epinephrine_postCPB = if_else(Label == 'Epinephrine' & Time > CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Epinephrine_postCPB= if_else(Label == 'Epinephrine'& Time > CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate('Norepinephrine(800/50)_postCPB'= if_else(Label == 'Norepinephrine (800/50)' & Time > CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate('Norepinephrine_postCPB'= if_else(Label == 'Norepinephrine' & Time > CPB_End_Time ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Vasopressin_postCPB= if_else(Label == 'Vasopressin' & Time > CPB_End_Time ,1,0))

#total
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Phenylephrine_total = if_else(Label == 'Phenylephrine' ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Epinephrine_total = if_else(Label == 'Epinephrine' ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Epinephrine_total= if_else(Label == 'Epinephrine',1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate('Norepinephrine(800/50)_total'= if_else(Label == 'Norepinephrine (800/50)' ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate('Norepinephrine_total'= if_else(Label == 'Norepinephrine' ,1,0))
BolusDrugsDF_CPBloc<-BolusDrugsDF_CPBloc %>% mutate(Vasopressin_total= if_else(Label == 'Vasopressin' ,1,0))

#We summarize the information so we just know if there was or not an infusion of a certain drug per CPB petiod per case

BolusDrugsDF_CPBloc_final<-subset(BolusDrugsDF_CPBloc, select = -c(2:8))

library(dplyr)

#preCPB
BolusDrugsDF_bloc_sum<-setNames(aggregate(BolusDrugsDF_CPBloc_final$Phenylephrine_preCPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Phenylephrine_bolus_preCPB"))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$Epinephrine_preCPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Epinephrine_bolus_preCPB")))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$`Norepinephrine(800/50)_preCPB`, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine(800/50)_bolus_preCPB')))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$`Norepinephrine_preCPB`, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine_bolus_preCPB')))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$Vasopressin_preCPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Vasopressin_bolus_preCPB')))


#CPB
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum,
setNames(aggregate(BolusDrugsDF_CPBloc_final$Phenylephrine_CPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Phenylephrine_bolus_CPB")))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$Epinephrine_CPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Epinephrine_bolus_CPB")))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$`Norepinephrine(800/50)_CPB`, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine(800/50)_bolus_CPB')))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$`Norepinephrine_CPB`, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine_bolus_CPB')))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$Vasopressin_CPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Vasopressin_bolus_CPB')))


#postCPB
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum,
setNames(aggregate(BolusDrugsDF_CPBloc_final$Phenylephrine_postCPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Phenylephrine_bolus_postCPB")))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$Epinephrine_postCPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Epinephrine_bolus_postCPB")))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$`Norepinephrine(800/50)_postCPB`, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine(800/50)_bolus_postCPB')))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$`Norepinephrine_postCPB`, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine_bolus_postCPB')))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$Vasopressin_postCPB, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Vasopressin_bolus_postCPB')))

#total
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum,
setNames(aggregate(BolusDrugsDF_CPBloc_final$Phenylephrine_total, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Phenylephrine_bolus_total")))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$Epinephrine_total, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Epinephrine_bolus_total")))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$`Norepinephrine(800/50)_total`, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine(800/50)_bolus_total')))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$`Norepinephrine_total`, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine_bolus_total')))
BolusDrugsDF_bloc_sum<-merge(BolusDrugsDF_bloc_sum, setNames(aggregate(BolusDrugsDF_CPBloc_final$Vasopressin_total, by=list(Case_Name=BolusDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Vasopressin_bolus_total')))


#in the following code we get rid of the quantity and convert it to boolean
BolusDrugs.bin<-replace(BolusDrugsDF_bloc_sum, BolusDrugsDF_bloc_sum > 0, 1)
BolusDrugs.bin<-sapply(BolusDrugs.bin, as.factor)
BolusDrugs.bin<-as.data.frame(BolusDrugs.bin)

#we exclude those cases not present in our cohort (STS+AIMS join)
BolusDrugs.bin<-inner_join(, BolusDrugs.bin)


```


# OLD Infusion Drugs

## Infusion Drugs quantities

```{r eval=FALSE, include=FALSE}
library(dplyr)

InfusionDrugsDF <- rbind(InfusionDrugs08, InfusionDrugs09, InfusionDrugs10,InfusionDrugs11,InfusionDrugs12,InfusionDrugs13,InfusionDrugs14,InfusionDrugs15,InfusionDrugs16)

#InfusionDrugsDF$Time<-NULL
InfusionDrugsDF$ItemID<-NULL
InfusionDrugsDF$Route<-NULL
InfusionDrugsDF$ESIG<-NULL
InfusionDrugsDF$ESIGNAMETEXT<-NULL
InfusionDrugsDF$ESIGDATEANDTIME<-NULL

#unique(InfusionDrugsDF$Label)

InfusionDrugsDF<-InfusionDrugsDF %>% mutate(Phenylephrine= if_else(Label == 'Phenylephrine',1,0))
InfusionDrugsDF<-InfusionDrugsDF %>% mutate(Epinephrine= if_else(Label == 'Epinephrine',1,0))
InfusionDrugsDF<-InfusionDrugsDF %>% mutate('Norepinephrine (800/50)'= if_else(Label == 'Norepinephrine (800/50)' ,1,0))
InfusionDrugsDF<-InfusionDrugsDF %>% mutate('Norepinephrine'= if_else(Label == 'Norepinephrine' ,1,0))
InfusionDrugsDF<-InfusionDrugsDF %>% mutate('Vasopressin'= if_else(Label == 'Vasopressin' ,1,0))




library(reshape)

Infusiondrugspercase<-reshape(InfusionDrugsDF, timevar = 'Label' , idvar = 'Case_Name', direction = 'wide')

#barplot(table(InfusionDrugsDF$Units[InfusionDrugsDF$Label=='Phenylephrine']))

```

## Infusion Drugs binary CPB location

```{r eval=FALSE, include=FALSE}
library(dplyr)

InfusionDrugsDF_CPBloc<- rbind(InfusionDrugs08, InfusionDrugs09, InfusionDrugs10,InfusionDrugs11,InfusionDrugs12,InfusionDrugs13,InfusionDrugs14,InfusionDrugs15,InfusionDrugs16)

#After creating our DF, let's perform our filtering and table reshape

InfusionDrugsDF_CPBloc<-subset(InfusionDrugsDF_CPBloc, InfusionDrugsDF_CPBloc$Label!='Calcium Chloride' & InfusionDrugsDF_CPBloc$Label != 'Calcium Gluconate')

#InfusionDrugsDF_CPBloc$Time<-NULL
InfusionDrugsDF_CPBloc$ItemID<-NULL
InfusionDrugsDF_CPBloc$Route<-NULL
InfusionDrugsDF_CPBloc$ESIG<-NULL
InfusionDrugsDF_CPBloc$ESIGNAMETEXT<-NULL
InfusionDrugsDF_CPBloc$ESIGDATEANDTIME<-NULL

#merge the datasets we need
InfusionDrugsDF_CPBloc<-merge(InfusionDrugsDF_CPBloc, rCPBEventsDF)

##Add the bypass begin and end for comparation

#preCPB
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Phenylephrine_preCPB = if_else(Label == 'Phenylephrine' & Time < CPB_Begin_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Epinephrine_preCPB = if_else(Label == 'Epinephrine' & Time < CPB_Begin_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Epinephrine_preCPB= if_else(Label == 'Epinephrine'& Time < CPB_Begin_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate('Norepinephrine(800/50)_preCPB'= if_else(Label == 'Norepinephrine (800/50)' & Time < CPB_Begin_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate('Norepinephrine_preCPB'= if_else(Label == 'Norepinephrine' & Time < CPB_Begin_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Vasopressin_preCPB= if_else(Label == 'Vasopressin' & Time < CPB_Begin_Time ,1,0))


#CPB
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Phenylephrine_CPB = if_else(Label == 'Phenylephrine' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Epinephrine_CPB = if_else(Label == 'Epinephrine' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Epinephrine_CPB= if_else(Label == 'Epinephrine'& Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate('Norepinephrine(800/50)_CPB'= if_else(Label == 'Norepinephrine (800/50)' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate('Norepinephrine_CPB'= if_else(Label == 'Norepinephrine' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Vasopressin_CPB= if_else(Label == 'Vasopressin' & Time >= CPB_Begin_Time & Time <= CPB_End_Time ,1,0))


#postCPB
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Phenylephrine_postCPB = if_else(Label == 'Phenylephrine' & Time > CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Epinephrine_postCPB = if_else(Label == 'Epinephrine' & Time > CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Epinephrine_postCPB= if_else(Label == 'Epinephrine'& Time > CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate('Norepinephrine(800/50)_postCPB'= if_else(Label == 'Norepinephrine (800/50)' & Time > CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate('Norepinephrine_postCPB'= if_else(Label == 'Norepinephrine' & Time > CPB_End_Time ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Vasopressin_postCPB= if_else(Label == 'Vasopressin' & Time > CPB_End_Time ,1,0))

#total
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Phenylephrine_total = if_else(Label == 'Phenylephrine' ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Epinephrine_total = if_else(Label == 'Epinephrine' ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Epinephrine_total= if_else(Label == 'Epinephrine',1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate('Norepinephrine(800/50)_total'= if_else(Label == 'Norepinephrine (800/50)' ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate('Norepinephrine_total'= if_else(Label == 'Norepinephrine' ,1,0))
InfusionDrugsDF_CPBloc<-InfusionDrugsDF_CPBloc %>% mutate(Vasopressin_total= if_else(Label == 'Vasopressin' ,1,0))

#We summarize the information so we just know if there was or not an infusion of a certain drug per CPB petiod per case

InfusionDrugsDF_CPBloc_final<-subset(InfusionDrugsDF_CPBloc, select = -c(2:8))

library(dplyr)

#preCPB
InfusionDrugsDF_bloc_sum<-setNames(aggregate(InfusionDrugsDF_CPBloc_final$Phenylephrine_preCPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Phenylephrine_Infusion_preCPB"))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$Epinephrine_preCPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Epinephrine_Infusion_preCPB")))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$`Norepinephrine(800/50)_preCPB`, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine(800/50)_Infusion_preCPB')))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$`Norepinephrine_preCPB`, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine_Infusion_preCPB')))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$Vasopressin_preCPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Vasopressin_Infusion_preCPB')))


#CPB
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum,
setNames(aggregate(InfusionDrugsDF_CPBloc_final$Phenylephrine_CPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Phenylephrine_Infusion_CPB")))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$Epinephrine_CPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Epinephrine_Infusion_CPB")))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$`Norepinephrine(800/50)_CPB`, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine(800/50)_Infusion_CPB')))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$`Norepinephrine_CPB`, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine_Infusion_CPB')))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$Vasopressin_CPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Vasopressin_Infusion_CPB')))


#postCPB
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum,
setNames(aggregate(InfusionDrugsDF_CPBloc_final$Phenylephrine_postCPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Phenylephrine_Infusion_postCPB")))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$Epinephrine_postCPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Epinephrine_Infusion_postCPB")))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$`Norepinephrine(800/50)_postCPB`, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine(800/50)_Infusion_postCPB')))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$`Norepinephrine_postCPB`, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine_Infusion_postCPB')))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$Vasopressin_postCPB, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Vasopressin_Infusion_postCPB')))

#total
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum,
setNames(aggregate(InfusionDrugsDF_CPBloc_final$Phenylephrine_total, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Phenylephrine_Infusion_total")))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$Epinephrine_total, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", "Epinephrine_Infusion_total")))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$`Norepinephrine(800/50)_total`, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine(800/50)_Infusion_total')))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$`Norepinephrine_total`, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Norepinephrine_Infusion_total')))
InfusionDrugsDF_bloc_sum<-merge(InfusionDrugsDF_bloc_sum, setNames(aggregate(InfusionDrugsDF_CPBloc_final$Vasopressin_total, by=list(Case_Name=InfusionDrugsDF_CPBloc_final$Case_Name), FUN=sum), c("Case_Name", 'Vasopressin_Infusion_total')))


#in the following code we get rid of the quantity and convert it to boolean
InfusionDrugs.bin<-replace(InfusionDrugsDF_bloc_sum, InfusionDrugsDF_bloc_sum > 0, 1)
InfusionDrugs.bin<-sapply(InfusionDrugs.bin, as.factor)

InfusionDrugs.bin<-as.data.frame(InfusionDrugs.bin)



```


```{r}
generate_vasopressors <- function(epinephrine_total, norepinephrine_total, phenylephrine_total ){
generate_vasopressors = epinephrine_total + norepinephrine_total + (phenylephrine_total/10)
return(generate_vasopressors)
}
```

# OLD Units normalization

## Study data
```{r eval=FALSE, include=FALSE}
library(dplyr)
BolusDrugsDF %>% 
  group_by(Label, Units)  %>% 
  summarise(n = n()) %>%
  arrange(Label,desc(n))

library(dplyr)
InfusionDrugsDF %>% 
  group_by(Label, Dose_Units)  %>% 
  summarise(n = n()) %>%
  arrange(Label,desc(n))

```


# OLD Groups

## Calculating total doses in group A pressors per case

```{r eval=FALSE, include=FALSE}
library(plyr)
detach(package:plyr)
library(dplyr)
drugTotalspercase_and_drug<-subset(DrugTotals_forstudy, Group=='A') %>%
    group_by(CASENUMBER, DRUGTEXT) %>%
  mutate(total_drug = cumsum(converted_dose_mg))

drugs_groupA_percase<-drugTotalspercase_and_drug %>% group_by(CASENUMBER) %>% dplyr::summarize(total_groupA = max(total_drug))

names(drugs_groupA_percase)[1]<-'Case_Name'
      
```

## Calculating total doses in group B pressors per case

```{r eval=FALSE, include=FALSE}
library(dplyr)
drugTotalspercase_and_drug<-subset(DrugTotals_forstudy, Group=='B') %>%
    group_by(CASENUMBER) %>%
  mutate(total_drug = cumsum(converted_dose_mg))

drugs_groupB_percase<-drugTotalspercase_and_drug %>% group_by(CASENUMBER) %>% summarise(total_groupB = max(total_drug))

names(drugs_groupB_percase)[1]<-'Case_Name'     
```









