
---
title: "Quantiles"
author: "Miguel Ángel Armengol de la Hoz"
output:
  html_document:
    toc: true
    theme: united
---

# Environment

```{r}
library(dplyr)
library(plotly)
library(corrplot)
library(Hmisc)
#library(officer)
library(xlsx)
library(plot3D)
library(ggeffects)
library(mgcv)
library(tidyverse)
library(mgcViz)
```



```{r setup, include=FALSE}
#load the data
#load("C:/BIG FILES/Phenotyping/HemodynamicProjectsDatasetFeb18.RData")
```


# Plots

## Wrangling the dataset for plotting

Now we are using RFDS as output instead of MAE.

```{r eval=FALSE, include=FALSE}
###IMPORTANT detach plyr!!
#detach('package:plyr')


# AUC Quartiles 


Q_AUC65MAP_total_mmHgmin_pressors_RFDS<-FinalHemodynamicsDataset%>%
dplyr::group_by(Q_AUC65MAP_total_mmHgmin, Q_total_pressors_formula_mg) %>%
dplyr::summarise('RFDS rate (%)'=sum(RFDS)/274*100)
Q_AUC65MAP_total_mmHgmin_pressors_RFDS<-Q_AUC65MAP_total_mmHgmin_pressors_RFDS[complete.cases(Q_AUC65MAP_total_mmHgmin_pressors_RFDS), ]

library(reshape)
Q_AUC65MAP_total_mmHgmin_pressors_RFDS_matrix<-cast(data=Q_AUC65MAP_total_mmHgmin_pressors_RFDS
     ,Q_AUC65MAP_total_mmHgmin ~ Q_total_pressors_formula_mg
     ,value = 'RFDS rate (%)')
Q_AUC65MAP_total_mmHgmin_pressors_RFDS_matrix<-as.data.frame(Q_AUC65MAP_total_mmHgmin_pressors_RFDS_matrix)
colnames(Q_AUC65MAP_total_mmHgmin_pressors_RFDS_matrix)<-c('','total pressors Q1','total pressors Q2','total pressors Q3','total pressors Q4')
rownames(Q_AUC65MAP_total_mmHgmin_pressors_RFDS_matrix)<-c('total AUC65 MAP  Q1','total AUC65 MAP  Q2','total AUC65 MAP  Q3','total AUC65 MAP  Q4')
Q_AUC65MAP_total_mmHgmin_pressors_RFDS_matrix[,1]<-NULL
Q_AUC65MAP_total_mmHgmin_pressors_RFDS_matrix<-round(Q_AUC65MAP_total_mmHgmin_pressors_RFDS_matrix,2)


```

# 3D Plots Data

## Exporting to excel

```{r}
# AUC
write.xlsx(Q_AUC65MAP_total_mmHgmin_pressors_MAE_matrix,
'Q_AUC65MAP_total_mmHgmin_pressors_MAE_matrix.xlsx')
```


# 3D Tertiles in R

```{r}
hist3D( main =  paste("T AUT50MAP Plot\n Number of Cases =", sum(T_AUT50MAP_total_min_pressors_MAE_matrix))
   , x = c(1:3)
   , y = c(1:3)
   , z = T_AUT50MAP_total_min_pressors_MAE_matrix
   , scale = F, expand = 0.01, bty = "b2", phi = 20, col = "#1e8bc3"
   , border = "white", shade = 0.5, ltheta = 90
   , space = 0.3 #space between bars
   , ticktype = "detailed", d = 2
   ,resfac=3 #resolution
   ,xlab='T AUT50MAP total'
   ,ylab='T total pressors'
   ,zlab='patients with Any MAE'
   ,zlim=c(0,170))

hist3D( main =  paste("T AUT65MAP Plot\n Number of Cases =", sum(T_AUT65MAP_total_min_pressors_MAE_matrix))
   , x = c(1:3)
   , y = c(1:3)
   , z = T_AUT65MAP_total_min_pressors_MAE_matrix
   , scale = F, expand = 0.01, bty = "b2", phi = 20, col = "#1e8bc3"
   , border = "white", shade = 0.5, ltheta = 90
   , space = 0.3 #space between bars
   , ticktype = "detailed", d = 2
   ,resfac=3 #resolution
   ,xlab='T AUT65MAP total'
   ,ylab='T total pressors'
   ,zlab='patients with Any MAE'
   ,zlim=c(0,170))

# Make the rgl version
# Animated version
# library("plot3Drgl")
# plotrgl()
```

# 3D Quartiles in R

```{r}
library('plot3D')

hist3D( main =  paste("Q AUT50MAP Plot\n Number of Cases =", sum(Q_AUT50MAP_total_min_pressors_MAE_matrix))
   , x = c(1:4)
   , y = c(1:4)
   , z = Q_AUT50MAP_total_min_pressors_MAE_matrix
   , scale = F, expand = 0.01, bty = "b2", phi = 20, col = "#1e8bc3"
   , border = "white", shade = 0.5, ltheta = 90
   , space = 0.3 #space between bars
   , ticktype = "detailed", d = 2
   ,resfac=3 #resolution
   ,xlab='Q AUT50MAP total'
   ,ylab='Q total pressors'
   ,zlab='patients with Any MAE'
   ,zlim=c(0,170))

hist3D( main =  paste("Q AUT65MAP Plot\n Number of Cases =", sum(Q_AUT65MAP_total_min_pressors_MAE_matrix))
   , x = c(1:4)
   , y = c(1:4)
   , z = Q_AUT65MAP_total_min_pressors_MAE_matrix
   , scale = F, expand = 0.01, bty = "b2", phi = 20, col = "#1e8bc3"
   , border = "white", shade = 0.5, ltheta = 90
   , space = 0.3 #space between bars
   , ticktype = "detailed", d = 2
   ,resfac=3 #resolution
   ,xlab='Q AUT65MAP total'
   ,ylab='Q total pressors'
   ,zlab='patients with Any MAE'
   ,zlim=c(0,170))


```

# 2D Plots

## Quartiles

## Q_AUT50MAP_total_min_pressors_MAE 2D test

### Q_AUT50MAP_total_min

```{r eval=FALSE, include=FALSE}
library(plotly)
library(dplyr)
library(scales)
  
p1<-Q_AUT50MAP_total_min_pressors_MAE %>%
  dplyr::filter(Q_total_pressors_formula_mg==1) %>%
  dplyr::group_by(Q_AUT50MAP_total_min) %>%
  dplyr::summarise(total_patientswith_MAE=sum(total_patientswith_MAE)) %>%
  plot_ly(  x = ~Q_AUT50MAP_total_min
          , y= ~total_patientswith_MAE
          , type = 'bar'
          , marker = list(color = brewer_pal(palette="OrRd")(9)[5] )
          , name = 'Q1 pressors(mg) '
          ) %>%layout(  yaxis = list(range = c(0, 170))    )

p2<-Q_AUT50MAP_total_min_pressors_MAE %>%
  dplyr::filter(Q_total_pressors_formula_mg==2) %>%
  dplyr::group_by(Q_AUT50MAP_total_min) %>%
  dplyr::summarise(total_patientswith_MAE=sum(total_patientswith_MAE)) %>%
  plot_ly(  x = ~Q_AUT50MAP_total_min
          , y = ~total_patientswith_MAE
          , type = 'bar'
          , marker = list(color = brewer_pal(palette="OrRd")(9)[6] )
          , name = 'Q2 pressors(mg) '
          ) %>%layout(  yaxis = list(range = c(0, 170))    )

p3<-Q_AUT50MAP_total_min_pressors_MAE %>%
  dplyr::filter(Q_total_pressors_formula_mg==3) %>%
  dplyr::group_by(Q_AUT50MAP_total_min) %>%
  dplyr::summarise(total_patientswith_MAE=sum(total_patientswith_MAE)) %>%
  plot_ly(  x = ~Q_AUT50MAP_total_min
          , y = ~total_patientswith_MAE
          , type = 'bar'
          , marker = list(color = brewer_pal(palette="OrRd")(9)[7] )
          , name = 'Q3 pressors(mg) '
          ) %>%layout(  yaxis = list(range = c(0, 170))    )

p4<-Q_AUT50MAP_total_min_pressors_MAE %>%
  dplyr::filter(Q_total_pressors_formula_mg==4) %>%
  dplyr::group_by(Q_AUT50MAP_total_min) %>%
  dplyr::summarise(total_patientswith_MAE=sum(total_patientswith_MAE)) %>%
  plot_ly(  x = ~Q_AUT50MAP_total_min
          , y = ~total_patientswith_MAE
          , type = 'bar'
          , marker = list(color = brewer_pal(palette="OrRd")(9)[8] )
          , name = 'Q4 pressors(mg) '
          ) %>%layout(  yaxis = list(range = c(0, 170))    )

library(plotly)
plotly::subplot(p1, p2, p3, p4,nrows = 2,titleY = T,titleX = T,shareX = T,shareY = T) %>% 
   layout(
       title = paste('Total_Patients with Any_MAE: ', sum(Q_AUT50MAP_total_min_pressors_MAE$total_patientswith_MAE))
     )

```


### Q_total_pressors_formula_mg

```{r}
library(plotly)
library(dplyr)
library(scales)
  
p1<-Q_AUT50MAP_total_min_pressors_MAE %>%
  dplyr::filter(Q_AUT50MAP_total_min==1) %>%
  dplyr::group_by(Q_total_pressors_formula_mg) %>%
  dplyr::summarise(total_patientswith_MAE=sum(total_patientswith_MAE)) %>%
  plot_ly(    x = ~Q_total_pressors_formula_mg
          , y= ~total_patientswith_MAE
          , type = 'bar'
          , marker = list(color = brewer_pal(palette="Blues")(9)[5] )
          , name = 'Q1 AUT50MAP (mins) '
          ) %>%layout(  yaxis = list(range = c(0, 170))    )

p2<-Q_AUT50MAP_total_min_pressors_MAE %>%
  dplyr::filter(Q_AUT50MAP_total_min==2) %>%
  dplyr::group_by(Q_total_pressors_formula_mg) %>%
  dplyr::summarise(total_patientswith_MAE=sum(total_patientswith_MAE)) %>%
  plot_ly(    x = ~Q_total_pressors_formula_mg
          , y = ~total_patientswith_MAE
          , type = 'bar'
          , marker = list(color = brewer_pal(palette="Blues")(9)[6] )
          , name = 'Q2 AUT50MAP (mins) '
          ) %>%layout(  yaxis = list(range = c(0, 170))    )

p3<-Q_AUT50MAP_total_min_pressors_MAE %>%
  dplyr::filter(Q_AUT50MAP_total_min==3) %>%
  dplyr::group_by(Q_total_pressors_formula_mg) %>%
  dplyr::summarise(total_patientswith_MAE=sum(total_patientswith_MAE)) %>%
  plot_ly(    x = ~Q_total_pressors_formula_mg
          , y = ~total_patientswith_MAE
          , type = 'bar'
          , marker = list(color = brewer_pal(palette="Blues")(9)[7] )
          , name = 'Q3 AUT50MAP (mins) '
          ) %>%layout(  yaxis = list(range = c(0, 170))    )

p4<-Q_AUT50MAP_total_min_pressors_MAE %>%
  dplyr::filter(Q_AUT50MAP_total_min==4) %>%
  dplyr::group_by(Q_total_pressors_formula_mg) %>%
  dplyr::summarise(total_patientswith_MAE=sum(total_patientswith_MAE)) %>%
  plot_ly(    x = ~Q_total_pressors_formula_mg
          , y = ~total_patientswith_MAE
          , type = 'bar'
          , marker = list(color = brewer_pal(palette="Blues")(9)[8] )
          , name = 'Q4 AUT50MAP (mins) '
          ) %>%layout(  yaxis = list(range = c(0, 170))    )
library(plotly)
pfinal<-plotly::subplot(p1, p2, p3, p4,nrows = 2,titleY = T,titleX = T,shareX = T,shareY = T) %>% 
   layout(
       title = paste('Total_Patients with Any_MAE: ', sum(Q_AUT50MAP_total_min_pressors_MAE$total_patientswith_MAE))
     )

```

# Boxplot for all the bands MAP

```{r}
library(dplyr)
library(plotly)
library(RColorBrewer)
palette <- brewer.pal(9, "Set1")

# annotations
a <- list(
  text = "Mean Arterial Pressure Bands and time in minutes patients spent on that band.",
  font = list(size = 16),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

x <- list( title = "Total time spent in a given threshold (min)" )
p1 <- plot_ly(y = FinalHemodynamicsDataset[FinalHemodynamicsDataset$Any_MAE==0,]$AUT65MAP_total_min, type = "box",name = "<65 No MAE"
               ,marker = list(color = '#2ecc71'),opacity = 0.8, line = list(color = '#27ae60')) %>%
  add_trace(y = FinalHemodynamicsDataset[FinalHemodynamicsDataset$Any_MAE==1,]$AUT65MAP_total_min,name = "<65 Any MAE"
               ,marker = list(color = '#e74c3c'),opacity = 0.8, line = list(color = '#c0392b')) %>%  
  
  add_trace(y = FinalHemodynamicsDataset[FinalHemodynamicsDataset$Any_MAE==0,]$AOT65MAP_total_min,name = ">65 No MAE"
               ,marker = list(color = '#2ecc71'),opacity = 0.8, line = list(color = '#27ae60')) %>%
  add_trace(y = FinalHemodynamicsDataset[FinalHemodynamicsDataset$Any_MAE==1,]$AOT65MAP_total_min,name = ">65 Any MAE"
               ,marker = list(color = '#e74c3c'),opacity = 0.8, line = list(color = '#c0392b')) %>%

 


  layout(showlegend = F,xaxis = x
         #, yaxis = list(range=c(0,800))
         , annotations = a)  


#htmlwidgets::saveWidget(sp1, "boxplots.html")
```

# Boxplot for threshold <=65

```{r}
library(dplyr)
library(plotly)
library(RColorBrewer)
palette <- brewer.pal(9, "Set1")

# annotations
a <- list(
  text = "MAP < 65 mmHg duration per group",
  font = list(size = 16),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

y <- list( title = "Total duration (min)" )
x <- list( title = "Groups" )
p1 <- plot_ly(y = FinalHemodynamicsDataset[FinalHemodynamicsDataset$Any_MAE==0,]$AUT65MAP_total_min, type = "box",name = "Absent MAE"
               ,marker = list(color = '#2ecc71'),opacity = 0.8, line = list(color = '#27ae60')) %>%
  add_trace(y = FinalHemodynamicsDataset[FinalHemodynamicsDataset$Any_MAE==1,]$AUT65MAP_total_min,name = "Present MAE"
               ,marker = list(color = '#e74c3c'),opacity = 0.8, line = list(color = '#c0392b')) %>%  
  
  add_trace(y = FinalHemodynamicsDataset$AUT65MAP_total_min,name = "All patients"
               ,marker = list(color = '#2980b9'),opacity = 0.8, line = list(color = '#2980b9')) %>%    

  layout(showlegend = F
         , xaxis = x
         , yaxis = y
         , annotations = a)  

a <- list(
  text = "AUC MAP < 65 mmHg",
  font = list(size = 16),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

y <- list( title = "Area under the curve (mmHg•min)" )
x <- list( title = "Groups" )
p2 <- plot_ly(y = FinalHemodynamicsDataset[FinalHemodynamicsDataset$Any_MAE==0,]$AUC65MAP_total_mmHgmin, type = "box",name = "Absent MAE"
               ,marker = list(color = '#2ecc71'),opacity = 0.8, line = list(color = '#27ae60')) %>%
  add_trace(y = FinalHemodynamicsDataset[FinalHemodynamicsDataset$Any_MAE==1,]$AUC65MAP_total_mmHgmin,name = "Present MAE"
               ,marker = list(color = '#e74c3c'),opacity = 0.8, line = list(color = '#c0392b')) %>%  
  
  add_trace(y = FinalHemodynamicsDataset$AUC65MAP_total_mmHgmin,name = "All patients"
               ,marker = list(color = '#2980b9'),opacity = 0.8, line = list(color = '#2980b9')) %>%    

  layout(showlegend = F
         , xaxis = x
         , yaxis = y
         , annotations = a)  

#htmlwidgets::saveWidget(sp1, "boxplots.html")
```


# Correlations

Hi! I used "pearson"  since it is the default and I did not changed it since I did not know the distributions yet, now I know it I am going to use "spearman" since 
1) It is robust to outliers
2) It can be used with ordinal data as well

```{r}
relevant_data_for_corplot<-relevant_data[c('total_pressors_formula_mg', 'AUT65MAP_total_min', 'milrinone', 'Age', 'delta_HCT_pct_median_imp', 'mean_ef_median_imp', 'duration_Surgery_min', 'T_STS_RiskAlgorithm_multiple_imp', 'Cross_Clamp_Time_imp','Category','Gender' )]
relevant_data_for_corplot$Category <- as.numeric(plyr::revalue(relevant_data_for_corplot$Category , c( "CAB+other"=1, "CAB+valve+other"=2, "Valve+other"=3)) )
relevant_data_for_corplot$Gender <- as.numeric(plyr::revalue(relevant_data_for_corplot$Gender , c( "Male"=1, "Female"=2)) )
relevant_data_for_corplot$T_STS_RiskAlgorithm_multiple_imp<-as.numeric(relevant_data_for_corplot$T_STS_RiskAlgorithm_multiple_imp)

cor_variables<-cor(relevant_data_for_corplot, method = "spearman" )

#non interactive circle corplot
cortable<-corrplot(cor_variables, method = "number")

write.xlsx(as.data.frame(print(cortable)), "cortable.xlsx")

```


# Bubble plot

## Creating proper dataset
```{r}
Quartiles_dataframe_for_plot<-sqldf::sqldf(
  'SELECT
    Q_total_pressors_formula_mg
  , Q_AUT65MAP_total_min
  , COUNT(DISTINCT Case_Name) AS cases_in_group
  , SUM(RFDS)/COUNT(DISTINCT Case_Name) AS RFDS_percentage
  FROM
  FinalHemodynamicsDataset
  GROUP BY
  Q_total_pressors_formula_mg,Q_AUT65MAP_total_min
  '
)
```



```{r}
p <- plot_ly(Quartiles_dataframe_for_plot
             , x = ~as.character(Q_AUT65MAP_total_min)
             , y = ~as.character(Q_total_pressors_formula_mg)
             , text = ~round(RFDS_percentage,2)
             , textfont = list( size = 10
                                #,color = '#000000'
                                )
             , type = 'scatter'
             , mode = 'markers+text'
             , color = ~RFDS_percentage
             , size = ~RFDS_percentage
             , colors = c('#f1a9a087','#bd1200')
             , sizes = c(10, 120)
             , showlegend = F
             , marker = list(
                opacity = 1
          , sizemode = 'diameter')) %>%
  layout(
#title = 'Any MAE rate (%) for TWA-MAP under 65 mmHgNumber of cases = 518',
         xaxis = list(showgrid = T, title='Vasopressor-Inotrope dose\nQuartile'),
         yaxis = list(showgrid = T, title='Intraoperative hypotension total duration MAP <65mmHg\nQuartile'))

htmlwidgets::saveWidget(p, "bubbleplot.html")

```


# Plots with CI

```{r}
trace1 <- list(
  uid = "f04e3027-450f-457f-87ae-4b5f16d781ed", 
  mode = "lines+markers+text", 
  type = "scatter", 
  x = c("01<br>AUROC<br>STS","02<br>AUROC<br>RF"), 
  y = c( best_models_insights[2,]$AUROC
        ,best_models_insights[1,]$AUROC)
  ,marker = list(
    size = 12, 
    color = c("#c0392b","#27ae60")
  ),
  line = list(
    color = '#74b9ff'
    ),
  error_y = list(
    type = "data",
    color = c("#bdc3c7"), 
    symmetric = FALSE,
    visible = TRUE, 
    array = c( best_models_insights[2,]$`AUROC_uci` - best_models_insights[2,]$AUROC
              ,best_models_insights[1,]$`AUROC_uci` - best_models_insights[1,]$AUROC),
    
    arrayminus = c( best_models_insights[2,]$AUROC - best_models_insights[2,]$`AUROC_lci`
                   ,best_models_insights[1,]$AUROC - best_models_insights[1,]$`AUROC_lci`)
  ), 
  text = c("Esto es el texto")
)
trace2 <- list(
  uid = "f04e3027-450f-457f-87ae-4b5f16d781ed", 
  mode = "lines+markers+text", 
  type = "scatter", 
  x = c("03<br>AP<br>STS","04<br>AP<br>RF"), 
  y = c( best_models_insights[2,]$AP
        ,best_models_insights[1,]$AP)
  ,marker = list(
    size = 12, 
    color = c("#c0392b","#27ae60")
  ),
  line = list(
    color = '#74b9ff'
    ), 
  error_y = list(
    type = "data", 
    color = c("#bdc3c7"), 
    symmetric = FALSE,
    visible = TRUE, 
    array = c( best_models_insights[2,]$`AP_uci` - best_models_insights[2,]$AP
              ,best_models_insights[1,]$`AP_uci` - best_models_insights[1,]$AP),
    
    arrayminus = c( best_models_insights[2,]$AP - best_models_insights[2,]$`AP_lci`
                   ,best_models_insights[1,]$AP - best_models_insights[1,]$`AP_lci`)
  ), 
  text = c("Esto es el texto")
)
trace4 <- list(
  uid = "f04e3027-450f-457f-87ae-4b5f16d781ed", 
  mode = "lines+markers+text", 
  type = "scatter", 
  x = c("05<br>Specificity<br>STS","06<br>Specificity<br>RF"), 
  y = c(best_models_insights[2,]$Specificity
       ,best_models_insights[1,]$Specificity  )
  ,marker = list(
    size = 12, 
    color = c("#c0392b","#27ae60")
  ),
  line = list(
    color = '#74b9ff'
    ), 
  error_y = list(
    type = "data", 
    color = c("#bdc3c7"), 
    symmetric = FALSE,
    visible = TRUE, 
    array = c( best_models_insights[2,]$`Specificity_uci` - best_models_insights[2,]$Specificity
              ,best_models_insights[1,]$`Specificity_uci` - best_models_insights[1,]$Specificity),
    
    arrayminus = c( best_models_insights[2,]$Specificity - best_models_insights[2,]$`Specificity_lci`
                   ,best_models_insights[1,]$Specificity - best_models_insights[1,]$`Specificity_lci`)
  ), 
  text = c("Esto es el texto")
)
trace5 <- list(
  uid = "f04e3027-450f-457f-87ae-4b5f16d781ed", 
  mode = "lines+markers+text", 
  type = "scatter", 
  x = c("07<br>Sensitivity<br>STS","08<br>Sensitivity<br>RF"), 
  y = c(best_models_insights[2,]$Sensitivity
       ,best_models_insights[1,]$Sensitivity  )
  ,marker = list(
    size = 12, 
    color = c("#c0392b","#27ae60")
  ),
  line = list(
    color = '#74b9ff'
    ), 
  error_y = list(
    type = "data", 
    color = c("#bdc3c7"), 
    symmetric = FALSE,
    visible = TRUE, 
    array = c( best_models_insights[2,]$`Sensitivity_uci` - best_models_insights[2,]$Sensitivity
              ,best_models_insights[1,]$`Sensitivity_uci` - best_models_insights[1,]$Sensitivity),
    
    arrayminus = c( best_models_insights[2,]$Sensitivity - best_models_insights[2,]$`Sensitivity_lci`
                   ,best_models_insights[1,]$Sensitivity - best_models_insights[1,]$`Sensitivity_lci`)
  ), 
  text = c("Esto es el texto")
)


data <- list(trace1,trace2,trace4,trace5)
#layout <- list(title = "Performance Insights with 95% confidence interval")
p <- plot_ly()
p <- add_trace(p, uid=trace1$uid, mode=trace1$mode, type=trace1$type, x=trace1$x, y=trace1$y, marker=trace1$marker, line=trace1$line, error_y=trace1$error_y, text=paste(trace1$y,' CI [',trace1$y-trace1$error_y$arrayminus,',',trace1$y+trace1$error_y$array,']',sep = '') ,textposition = 'right')
p <- add_trace(p, uid=trace2$uid, mode=trace2$mode, type=trace2$type, x=trace2$x, y=trace2$y, marker=trace2$marker, line=trace2$line, error_y=trace2$error_y, text=paste(trace2$y,' CI [',trace2$y-trace2$error_y$arrayminus,',',trace2$y+trace2$error_y$array,']',sep = '') ,textposition = 'right')
p <- add_trace(p, uid=trace4$uid, mode=trace4$mode, type=trace4$type, x=trace4$x, y=trace4$y, marker=trace4$marker, line=trace4$line, error_y=trace4$error_y, text=paste(trace4$y,' CI [',trace4$y-trace4$error_y$arrayminus,',',trace4$y+trace4$error_y$array,']',sep = '') ,textposition = 'right')
p <- add_trace(p, uid=trace5$uid, mode=trace5$mode, type=trace5$type, x=trace5$x, y=trace5$y, marker=trace5$marker, line=trace5$line, error_y=trace5$error_y, text=paste(trace5$y,' CI [',trace5$y-trace5$error_y$arrayminus,',',trace5$y+trace5$error_y$array,']',sep = '') ,textposition = 'left')
p <- layout(p 
            #,title=layout$title
            ,showlegend=T
            ,yaxis = list(range = c(0, 1))
            )
```

# OR ggplot

```{r}
set.seed(0815)
df <- data.frame(x =1:10,
                 F =runif(10,1,2),
                 L =runif(10,0,1),
                 U =runif(10,2,3))

require(ggplot2)
ggplot(df, aes(x = x, y = F)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymax = U, ymin = L))
```

# Supplemental Figure 1 A

Primary analysis 1 trajectory

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_total_tenmins
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_tenmins
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)

predicted_data<-as.data.frame(ggeffect(mod_multiv,terms="AUT65MAP_total_tenmins"))
predicted_data[,c("predicted","std.error","conf.low","conf.high" )]<-predicted_data[,c("predicted","std.error","conf.low","conf.high" )]*100

ggplot(data=predicted_data, aes(x=x, y=predicted))+
    geom_line()+
    geom_ribbon(data=predicted_data,aes(x=x,ymin=conf.low,ymax=conf.high),alpha=0.3,inherit.aes=FALSE)+
    xlab('IOH total duration MAP < 65 mmHg (minutes)')+
    ylab('Predicted RFDS (%)')+
    #scale_color_manual(labels = c("Black", "White"), values = c("#1abc9c","#f1c40f"))+
    #scale_fill_manual(labels = c("Black", "White"), values = c("#1abc9c","#f1c40f"))+
    theme_minimal()  
```
# Supplemental Figure 1 B

Based on the visual inspection top 5% of patients with intraoperative hypotension are less linear
We present intraoperative hypotension duration without the top 5% of patients with intraoperative hypotension duration in ten minutes.

Primary analysis 1 trajectory

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}

cuttoff<-quantile(relevant_data$AUT65MAP_total_tenmins, 0.95)

mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_total_tenmins
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_tenmins
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = relevant_data %>% filter(AUT65MAP_total_tenmins<cuttoff)
            , family=binomial(link="logit"))

summary(mod_multiv)

predicted_data<-as.data.frame(ggeffect(mod_multiv,terms="AUT65MAP_total_tenmins"))
predicted_data[,c("predicted","std.error","conf.low","conf.high" )]<-predicted_data[,c("predicted","std.error","conf.low","conf.high" )]*100

ggplot(data=predicted_data, aes(x=x, y=predicted))+
    geom_line()+
    geom_ribbon(data=predicted_data,aes(x=x,ymin=conf.low,ymax=conf.high),alpha=0.3,inherit.aes=FALSE)+
    xlab('IOH total duration MAP < 65 mmHg (minutes)\n Excluding top 5% of IOH Values')+
    ylab('Predicted RFDS (%)')+
    #scale_color_manual(labels = c("Black", "White"), values = c("#1abc9c","#f1c40f"))+
    #scale_fill_manual(labels = c("Black", "White"), values = c("#1abc9c","#f1c40f"))+
    theme_minimal()  
```
# Supplemental Figure 3

Society of Thoracic Surgeons risk score and final cohort

```{r}
mod_multiv<-glm(RFDS ~ 
                  STS_RiskAlgorithm_median_imp
                 , data = relevant_data 
            , family=binomial(link="logit"))


predicted_data<-as.data.frame(ggeffect(mod_multiv,terms="STS_RiskAlgorithm_median_imp"))
predicted_data[,c("predicted","std.error","conf.low","conf.high" )]<-predicted_data[,c("predicted","std.error","conf.low","conf.high" )]*100

ggplot(data=predicted_data, aes(x=x, y=predicted))+
    geom_line()+
    geom_ribbon(data=predicted_data,aes(x=x,ymin=conf.low,ymax=conf.high),alpha=0.3,inherit.aes=FALSE)+
    xlab('STS risk score')+
    ylab('Predicted RFDS (%)')+
    #scale_color_manual(labels = c("Black", "White"), values = c("#1abc9c","#f1c40f"))+
    #scale_fill_manual(labels = c("Black", "White"), values = c("#1abc9c","#f1c40f"))+
    theme_minimal()  

```


# FIgure 3

# TEST 2 IOH Cat as main exposure

# Full Cohort

## Full Surgery Duration

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
#below_ninetyfith
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_total_min
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + STS_RiskAlgorithm_median_imp
                 + Cross_Clamp_Time_imp
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)


ggeffect(mod_multiv,terms="STS_RiskAlgorithm_median_imp") %>% plot()



oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"Predicted RFDS"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table

write.xlsx(as.data.frame(print(oddsratios_table)), "../Tables and Figures/oddsratios_table_exploratory4.xlsx")

```








### Exploratory analyses





####  Exploratory analysis 1

Outcome: Stroke
Exposure: main exposure IOH_cat

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +IOH_cat
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data_for_figure_3
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)

oddsratios_table


```

####  Exploratory analysis 2

Outcome: Renal Failure
Exposure: main exposure IOH_cat

```{r}
# Selecting reference levels for the categorical variables


mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +IOH_cat
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data_for_figure_3
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table


```

####  Exploratory analysis 3

Outcome: Death
Exposure: main exposure IOH_cat

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +IOH_cat
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data_for_figure_3
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table


```

