---
title: "Table1"
author: "Miguel Angel Armengol de la Hoz"
output: html_notebook
---


```{r setup, include=FALSE}
#load the data
#load("C:/BIG FILES/Phenotyping/HemodynamicProjectsDatasetFeb18.RData")
```

# Environment

```{r}
library(tableone)
library(magrittr)
library(xlsx)
library(dplyr)
library(oce)
'%!in%' <- function(x,y)!('%in%'(x,y))
```

Including fluid data only for table1 (not for modeling)

```{r}
FinalHemodynamicsDataset_for_table1<-FinalHemodynamicsDataset
FinalHemodynamicsDataset_for_table1<-left_join(FinalHemodynamicsDataset_for_table1,IO_data_Fluids_summarized)
```


# Table 1

test NonNormal: The default is kruskal.test (Kruskal-Wallis rank sum test). This is equivalent of the wilcox.test (ManWhitney U test) when there are only two groups.
test Normal: The default isoneway.test. This is equivalent of the t-test when there are only two groups.
test Categorical: A function used to perform the large sample approximation based tests. Thedefault is chisq.test.

```{r}
listVars
listVarstab1 <-
  c(
    listVars,
    "STS_RiskAlgorithm_multiple_imp",
    "delta_HCT_pct_median_imp",
    "mean_ef_median_imp",
    "Colloids_ml",
    "Crystalloids_ml",
    "Cross_Clamp_Time",
    "duration_CPB_tenmins",
    "AUT65MAP_total_tenmins",
    "AUC65MAP_total_mmHgtenmins",
    "total_pressors_formula_mg",
    "milrinone"
  )


catVars <- c(
  "Gender",
  "Category",
  #Background diseases
  "Diabetes",
  "RFDyslipidemia",
  "Hypertension_final",
  "Smoking",
  "Congestive_Heart_Failure",
  "Previous_myocardial_infarction",
  "ChronicLungDisease",
  "Dialysis",
  #Preoperative medications
  "PreOpMedBetaBlockers",
  "PreOpMedACEI_or_ARBs",
  "PreOpMedInotropes",
  "PreOpMedSteroids",
  "PreOpMedAspirin",
  "PreOpMedLipidLowering"
) #AKA statins

non_normal_variables<-c("STS_RiskAlgorithm_multiple_imp","delta_HCT_pct_median_imp","mean_ef_median_imp","Colloids_ml","Crystalloids_ml","Cross_Clamp_Time","duration_CPB_min","AUT65MAP_total_min","AUC65MAP_total_mmHgmin","total_pressors_formula_mg","milrinone")

table1 <- CreateTableOne(
  vars = listVarstab1,
  data = FinalHemodynamicsDataset_for_table1,
  factorVars = catVars,
  testNormal = oneway.test
  
  #strata is usefull in case we want several columns to stratify by
)

table1strat <- CreateTableOne(
  vars = listVarstab1,
  data = FinalHemodynamicsDataset_for_table1,
  factorVars = catVars,
  testNormal = oneway.test,
  strata = c("RFDS") #strata is useful in case we want several columns to stratify by
)
## non-normal specifies variables to be shown as median [IQR]



table1_printed <- as.data.frame(print(table1, nonnormal  = non_normal_variables))
table1strat_printed <- as.data.frame(print(table1strat, nonnormal  = non_normal_variables))

table1_final <- cbind(table1_printed, table1strat_printed)

write.xlsx(as.data.frame(print(table1_final)), "table1_final.xlsx")

```

# Suplemental Table 1 STS Excluded

## Identifying excluded patients

```{r}
FinalHemodynamicsDataset_for_table1_excluded<-CasesofInterestDF%>%filter(Case_Name %!in% FinalHemodynamicsDataset$Case_Name & Category %!in% c("CAB + Other","CAB + Valve + Other","Other","Valve + Other"))
```

# Exclusion Criteria

In our September resubmission we excluded aortic surgeries and other procedures per the reviewer recommendation (N=174).

```{r}
# we want to harmonize the Surgery Categories so we are going to
# 1 remove spaces from string
FinalHemodynamicsDataset_for_table1_excluded$Category<-gsub(" ", "", FinalHemodynamicsDataset_for_table1_excluded$Category, fixed = TRUE)

# 2 Format it all in tittle case
FinalHemodynamicsDataset_for_table1_excluded$Category<-titleCase(FinalHemodynamicsDataset_for_table1_excluded$Category)

# CAB is always in Capital
FinalHemodynamicsDataset_for_table1_excluded$Category<-gsub("Cab", "CAB", FinalHemodynamicsDataset_for_table1_excluded$Category, fixed = TRUE)

# CABG is always in Capital
FinalHemodynamicsDataset_for_table1_excluded$Category<-gsub("CABg", "CABG", FinalHemodynamicsDataset_for_table1_excluded$Category, fixed = TRUE)

# before exclusion
table(FinalHemodynamicsDataset_for_table1_excluded$Category)

FinalHemodynamicsDataset_for_table1_excluded<-FinalHemodynamicsDataset_for_table1_excluded%>%filter(Category!='Other')

# after exclusion
table(FinalHemodynamicsDataset_for_table1_excluded$Category)
```

# Combining Categories

Bala 092120:

we can merge CAB and CAB plus other as one.
CAB+VAlve and CAB+VAlve+other as one.
Valve and Valve plus other as Valve.

```{r}
# distribution before replacement
table(FinalHemodynamicsDataset_for_table1_excluded$Category)

FinalHemodynamicsDataset_for_table1_excluded$Category[ FinalHemodynamicsDataset_for_table1_excluded$Category%in% c('CAB','CABG') ]<-'CAB+other'

FinalHemodynamicsDataset_for_table1_excluded$Category[FinalHemodynamicsDataset_for_table1_excluded$Category=='CAB+valve']<-'CAB+valve+other'

FinalHemodynamicsDataset_for_table1_excluded$Category[FinalHemodynamicsDataset_for_table1_excluded$Category=='Valve']<-'Valve+other'

# distribution after replacement
table(FinalHemodynamicsDataset_for_table1_excluded$Category)

```

## Variable to stratify by creation and new datasets join

```{r}

listVarstab1
FinalHemodynamicsDataset_for_table1_excluded$excluded<-'1'

# we also need EF and HCT, so we need to retrieve them from their datasets
FinalHemodynamicsDataset_for_table1_excluded<-left_join(FinalHemodynamicsDataset_for_table1_excluded,Ejection_Fraction)
FinalHemodynamicsDataset_for_table1_excluded<-left_join(FinalHemodynamicsDataset_for_table1_excluded,All_HCT)
```



## Imputing missing data

### Mean EF

```{r}
FinalHemodynamicsDataset_for_table1_excluded['mean_ef_median_imp']<-if_else(
 is.na(FinalHemodynamicsDataset_for_table1_excluded$mean_ef)
,median(FinalHemodynamicsDataset_for_table1_excluded$mean_ef,na.rm = T)
,FinalHemodynamicsDataset_for_table1_excluded$mean_ef
)
```


### Delta HTC

```{r}
FinalHemodynamicsDataset_for_table1_excluded['delta_HCT_pct_median_imp']<-if_else(
 is.na(FinalHemodynamicsDataset_for_table1_excluded$delta_HCT_pct)
,median(FinalHemodynamicsDataset_for_table1_excluded$delta_HCT_pct,na.rm = T)
,FinalHemodynamicsDataset_for_table1_excluded$delta_HCT_pct
)
```

### Cross Clamp Time

```{r}
FinalHemodynamicsDataset_for_table1_excluded['Cross_Clamp_Time_imp']<-if_else(
 is.na(FinalHemodynamicsDataset_for_table1_excluded$Cross_Clamp_Time)
,median(FinalHemodynamicsDataset_for_table1_excluded$Cross_Clamp_Time,na.rm = T)
,FinalHemodynamicsDataset_for_table1_excluded$Cross_Clamp_Time
)
```

### STS_risk

We chose median imputation after having run the model with the best AUROC among all imputations.

```{r}

FinalHemodynamicsDataset_for_table1_excluded['STS_RiskAlgorithm_mean_imp']<-if_else(
 is.na(FinalHemodynamicsDataset_for_table1_excluded$STS_RiskAlgorithm)
,mean(FinalHemodynamicsDataset_for_table1_excluded$STS_RiskAlgorithm,na.rm = T)
,FinalHemodynamicsDataset_for_table1_excluded$STS_RiskAlgorithm
)
  
FinalHemodynamicsDataset_for_table1_excluded['STS_RiskAlgorithm_median_imp']<-ifelse(
 is.na(FinalHemodynamicsDataset_for_table1_excluded$STS_RiskAlgorithm)
,median(FinalHemodynamicsDataset_for_table1_excluded$STS_RiskAlgorithm,na.rm = T)
,FinalHemodynamicsDataset_for_table1_excluded$STS_RiskAlgorithm)
```

## Creating also new dataset including excluded and included patients together.

```{r}

listVarstab1 <-
  c(
    listVars,
    "STS_RiskAlgorithm",
    "delta_HCT_pct_median_imp",
    "mean_ef_median_imp",
    "Cross_Clamp_Time"
  )


catVars <- c(
  "Gender",
  "Category",
  #Background diseases
  "Diabetes",
  "RFDyslipidemia",
  "Hypertension_final",
  "Smoking",
  "Congestive_Heart_Failure",
  "Previous_myocardial_infarction",
  "ChronicLungDisease",
  "Dialysis",
  #Preoperative medications
  "PreOpMedBetaBlockers",
  "PreOpMedACEI_or_ARBs",
  "PreOpMedInotropes",
  "PreOpMedSteroids",
  "PreOpMedAspirin",
  "PreOpMedLipidLowering"
) #AKA statins

FinalHemodynamicsDataset_for_table1_excluded<-FinalHemodynamicsDataset_for_table1_excluded[listVarstab1]
FinalHemodynamicsDataset_for_table1_excluded$excluded<-'1'

FinalHemodynamicsDataset_for_table1_included<-FinalHemodynamicsDataset%>%filter(Case_Name %!in% FinalHemodynamicsDataset_for_table1_excluded$Case_Name)
FinalHemodynamicsDataset_for_table1_included<-FinalHemodynamicsDataset_for_table1_included[listVarstab1]


FinalHemodynamicsDataset_for_table1_included$excluded<-'0'

FinalHemodynamicsDataset_for_table1_excludedand_included<-rbind(FinalHemodynamicsDataset_for_table1_excluded,FinalHemodynamicsDataset_for_table1_included)
```


## Table generation

```{r}

table1 <- CreateTableOne(
  vars = listVarstab1,
  data = FinalHemodynamicsDataset_for_table1_excludedand_included,
  factorVars = catVars,
  testNormal = oneway.test
  
  #strata is usefull in case we want several columns to stratify by
)

table1strat <- CreateTableOne(
  vars = listVarstab1,
  data = FinalHemodynamicsDataset_for_table1_excludedand_included,
  factorVars = catVars,
  testNormal = oneway.test,
  strata = c("excluded") #strata is useful in case we want several columns to stratify by
)
## non-normal specifies variables to be shown as median [IQR]

non_normal_variables<-c("STS_RiskAlgorithm_multiple_imp","delta_HCT_pct_median_imp","mean_ef_median_imp","Cross_Clamp_Time")


table1_printed <- as.data.frame(print(table1, nonnormal  = non_normal_variables))
table1strat_printed <- as.data.frame(print(table1strat, nonnormal  = non_normal_variables))

table1_final <- cbind(table1_printed, table1strat_printed)

write.xlsx(as.data.frame(print(table1_final)), "sup_table1_excluded.xlsx")

```



