---
title: "Models creation"
author: "Miguel Ángel Armengol de la Hoz"
output:
  html_document:
    toc: true
    theme: united
---

# Libraries

```{r}
library(readr)
library(dplyr)
library(Amelia)
library(ggplot2)
library(xlsx)
library(Hmisc)
library(ResourceSelection)
library(rms)
#sudo ln -f -s $(/usr/libexec/java_home)/jre/lib/server/libjvm.dylib /usr/local/lib
library(rJava)
library(Deducer)
require(MASS)
```

# Creating dataset to fit logistc regression model

```{r}
#detach('pachage::dplyr')

relevant_data<-FinalHemodynamicsDataset%>%
dplyr::select( Case_Name
               ,Any_MAE
              ,Gender
              ,Age
              ,Category
              ,duration_Surgery_min
              ,T_STS_RiskAlgorithm_median_imp
              ,total_pressors_formula_mg
              ,AUT50MAP_total_min
              ,Q_AUT50MAP_total_min
              ,Q_total_pressors_formula_mg
              ,Q_AUT65MAP_total_min
              ,Q_AOT65MAP_total_min
              ,AUT65MAP_total_min
              ,AOT65MAP_total_min
              ,delta_HCT_pct_median_imp
              ,mean_ef_median_imp
              ,AUC65MAP_total_mmHgmin
              ,TWA65MAP_total_mmHg
              ,Q_AUC65MAP_total_mmHgmin
              ,Q_TWA65MAP_total_mmHg
              ,Q_AOC65MAP_total_mmHgmin
              ,Cross_Clamp_Time_imp
              ,duration_CPB_min
              ,AUC65MAP_CPB_total_mmHgmin
              )
```

# Factorizing Variables

```{r}
# Other variables to be factorized
relevant_data$Gender<-as.factor(relevant_data$Gender)
relevant_data$Category<-as.factor(relevant_data$Category)
relevant_data$Any_MAE<-as.factor(relevant_data$Any_MAE)

# Factorizing Quarrtiles
relevant_data$Q_AUT50MAP_total_min<-as.factor(relevant_data$Q_AUT50MAP_total_min)
relevant_data$Q_AUT65MAP_total_min<-as.factor(relevant_data$Q_AUT65MAP_total_min)
relevant_data$Q_AUT65MAP_total_min<-as.factor(relevant_data$Q_AUT65MAP_total_min)
relevant_data$Q_AOT65MAP_total_min<-as.factor(relevant_data$Q_AOT65MAP_total_min)
relevant_data$Q_total_pressors_formula_mg<-as.factor(relevant_data$Q_total_pressors_formula_mg)
relevant_data$Q_AUC65MAP_total_mmHgmin<-as.factor(relevant_data$Q_AUC65MAP_total_mmHgmin)
relevant_data$Q_AOC65MAP_total_mmHgmin<-as.factor(relevant_data$Q_AOC65MAP_total_mmHgmin)
relevant_data$Q_TWA65MAP_total_mmHg<-as.factor(relevant_data$Q_TWA65MAP_total_mmHg)

# Factorizing Tertiles
relevant_data$T_STS_RiskAlgorithm_median_imp<-as.factor(relevant_data$T_STS_RiskAlgorithm_median_imp)

#relevant_data$Q_AUT80SBP_total_min<-as.factor(relevant_data$Q_AUT80SBP_total_min)

# Factorizing tertiles
# relevant_data$T_AUT50MAP_total_min<-as.factor(relevant_data$T_AUT50MAP_total_min)
# relevant_data$T_AUT65MAP_total_min<-as.factor(relevant_data$T_AUT65MAP_total_min)
# relevant_data$T_AOT65MAP_total_min<-as.factor(relevant_data$T_AOT65MAP_total_min)
# relevant_data$T_total_pressors_formula_mg<-as.factor(relevant_data$T_total_pressors_formula_mg)

#relevant_data$Anesthesiologist<-as.factor(relevant_data$Anesthesiologist)

# creating T_STS_RiskAlgorithm_median_imp variable


```



# Multivariate log regression Tertiles of Pressors and MAP adjusted with offset and OR

```{r}
# Selecting reference levels for the categorical variables
relevant_data$Gender <- relevel(relevant_data$Gender, ref = "Male")
relevant_data$Category <- relevel(relevant_data$Category, ref = "CABG")

mod_multiv<-glm(Any_MAE ~ 
                 +Q_total_pressors_formula_mg
                 +Q_AUC65MAP_total_mmHgmin
                 +T_STS_RiskAlgorithm_median_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 #uncomment only for studying interaction (don't factorize variable Q when studying interaction)
                 +Q_AOC65MAP_total_mmHgmin*Q_total_pressors_formula_mg
                 #+offset(log(duration_Surgery_min))
                 +Cross_Clamp_Time_imp
                 #+as.factor(as.numeric(cut2(Cross_Clamp_Time, g=4)))
                 #+duration_CPB_min
                 ,family='binomial'
                 ,data = relevant_data
                )

mod_multiv

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1


write.xlsx(as.data.frame(print(oddsratios_table)), "/Users/marmengol/MEGA/Boston/BIDMC-Harvard/Phenotyping/Tables and Figures/oddsratios_table.xlsx")

```

## Evaluating the model

### AUC

```{r}
ROC<-rocplot(mod_multiv)
cat('AUC: ')
ROC$plot_env$auc
```

### Hosmer-Lemeshow goodness of fit test

If the p-value is too small, we don’t have to include it, given the conservative property of the test. If it’s larger than 0.05, we include it in the manuscript to make it more complete.

```{r}
hoslem.test(mod_multiv$y, fitted(mod_multiv),g=10)
```


# Exploratory analysis

## New model for STS risk ratio tertile 3

```{r}
# Selecting reference levels for the categorical variables
relevant_data$Gender <- relevel(relevant_data$Gender, ref = "Male")
relevant_data$Category <- relevel(relevant_data$Category, ref = "CABG")

relevant_data_STSrisk3<-subset(relevant_data, T_STS_RiskAlgorithm_median_imp==3)
  

mod_multiv<-glm(Any_MAE ~ 
                 +Q_total_pressors_formula_mg
                 +Q_AUC65MAP_total_mmHgmin
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 #uncomment only for studying interaction (don't factorize variable Q when studying interaction)
                 #+Q_AOC65MAP_total_mmHgmin*Q_total_pressors_formula_mg
                 #+offset(log(duration_Surgery_min))
                 +Cross_Clamp_Time_imp
                 #+as.factor(as.numeric(cut2(Cross_Clamp_Time, g=4)))
                 #+duration_CPB_min
                 ,family='binomial'
                 ,data = relevant_data_STSrisk3
                )

oddsratios_STST3_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_STST3_table<-round(oddsratios_STST3_table,4)
#oddsratios_STST3_table['x']<-(1:10)

oddsratios_STST3_table<-as.data.frame(oddsratios_STST3_table)
colnames(oddsratios_STST3_table)[1]<-"OR"

oddsratios_STST3_table<-oddsratios_STST3_table[order(row.names(oddsratios_STST3_table)), ]
boxLabels<-rownames(oddsratios_STST3_table)

write.xlsx(as.data.frame(print(oddsratios_STST3_table)), "/Users/marmengol/MEGA/Boston/BIDMC-Harvard/Phenotyping/Tables and Figures/oddsratios_STST3_table.xlsx")

```



# Studying the DataSet

```{r eval=FALSE, include=FALSE}
library(summarytools)
view(dfSummary(relevant_data))

test<-FinalHemodynamicsDataset %>%
  filter(AUT65MAP_total_ratio==0 & Any_MAE==1)
library(dplyr)
check<-inner_join(FinalHemodynamicsDataset,listofKeys)%>%
  filter(duration_Surgery_min>60) %>%
  dplyr::select(Case_Name,DOS,MRN,Sur_Begin_Time,Sur_End_Time,CPB_Begin_Time, CPB_End_Time, duration_preCPB_min, duration_CPB_min, duration_Surgery_min)



write.csv(check[1:10,],'highsurgerylength2.csv')

key1<-as.vector(unlist(unname(sapply(TextList, `[[`, 1)))) 
key2<-as.vector(unlist(unname(sapply(TextList, `[[`, 2)))) 
key3<-as.vector(unlist(unname(sapply(TextList, `[[`, 5))))  
key3<-as.numeric(test3)

listofKeys<-cbind.data.frame(key1,key2,key3)
listofKeys<-listofKeys[complete.cases(listofKeys),]
names(listofKeys)<-c('Case_Name','DOS','MRN')

df<-as.data.frame(key3,key1)
df['test']<-NA
df<-rename(df, eee = key3)
colnames(df)["key3"] ='eee'

  
colnames(df)["key3"]<-'eee'

names(df)['key3']

colnames(df)["name"]
colnames(df)['name']
```





