---
title: "Final Models"
author: Miguel Ángel Armengol de la Hoz
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_notebook:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float: no

knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(substr(inputFile,1,nchar(inputFile)-4)," ",Sys.Date(),'.html')) })
---

# Environment

```{r warning=FALSE}
library(readr)
library(dplyr)
library(Amelia)
library(ggplot2)
library(Hmisc)
library(ResourceSelection)
library(Deducer)
require(MASS)
library(lme4)
library(lmtest)
library(ggeffects)
library(xlsx)
library(car)
library(kableExtra)
library(modEvA)
# mean center and Standardization
meancstand <- function(x){
result<-as.numeric(scale(x,center=T, scale=T))
return(result)
}
```

# Creating dataset to fit logistc regression model

```{r}
#detach('pachage::dplyr')
FinalHemodynamicsDataset<-FinalHemodynamicsDataset%>%mutate(
AUT65MAP_outsideCPB_min=AUT65MAP_preCPB_min+AUT65MAP_postCPB_min,
AUT65MAP_outsideCPB_tenmins=AUT65MAP_preCPB_tenmins+AUT65MAP_postCPB_tenmins
)



relevant_data<-FinalHemodynamicsDataset%>%
dplyr::select( Case_Name
              ,Renal_Failure
              ,Any_MAE
              ,RFDS
              ,Stroke
              ,Death
              ,Gender
              ,Age
              ,Category
              ,duration_Surgery_min
              ,T_STS_RiskAlgorithm_multiple_imp
              ,T_STS_RiskAlgorithm_median_imp
              ,T_STS_RiskAlgorithm_multiple_imp
              ,STS_RiskAlgorithm_median_imp
              ,total_pressors_formula_mg
              ,AUT50MAP_total_min
              ,Q_AUT50MAP_total_min
              ,Q_total_pressors_formula_mg
              ,Q_AUT65MAP_total_min
              ,Q_AOT65MAP_total_min
              ,AUT65MAP_total_min
              ,delta_HCT_pct_median_imp
              ,mean_ef_median_imp
              ,AUC65MAP_total_mmHgmin
              ,TWA65MAP_total_mmHg
              ,Q_AUC65MAP_total_mmHgmin
              ,Q_TWA65MAP_total_mmHg
              ,Q_AOC65MAP_total_mmHgmin
              ,Cross_Clamp_Time_imp
              ,duration_CPB_min
              ,duration_outsideCPB_min
              ,AUC65MAP_CPB_mmHgmin
              ,Q_TWA65MAP_outsideCPB_mmHg
              ,Q_AUC65MAP_outsideCPB_mmHgmin
              ,Q_TWA65MAP_CPB_mmHg
              ,Q_AUC65MAP_CPB_mmHgmin
              ,Anesthesiologist
              ,IOH_cat
              ,Q_AUT65MAP_CPB_IOH_ratio
              ,Q_AUT65MAP_total_min
              ,AUT65MAP_outsideCPB_min
              ,AUT65MAP_preCPB_min
              ,AUT65MAP_CPB_min
              ,milrinone
              ,Diabetes                        
              ,Hypertension_final             
              ,Congestive_Heart_Failure       
              ,Previous_myocardial_infarction 
              ,ChronicLungDisease             
              ,Dialysis                       
              ,PreOpMedBetaBlockers           
              ,PreOpMedInotropes              
              ,PreOpMedSteroids               
              ,PreOpMedAspirin                
              ,PreOpMedLipidLowering          
              ,delta_HCT_pct_median_imp  
              ,mean_ef_median_imp    
              ,duration_CPB_min         
              ,AUT65MAP_total_min
              ,total_pressors_formula_mg
# tenmins              
              ,AUT65MAP_total_tenmins
              ,AUT65MAP_preCPB_tenmins
              ,AUT65MAP_CPB_tenmins
              ,AUT65MAP_postCPB_tenmins
              ,AUC65MAP_total_mmHgtenmins
              ,AOC65MAP_total_mmHgtenmins
              ,AUC65MAP_CPB_mmHgtenmins
              ,AUC65MAP_outsideCPB_mmHgtenmins
              ,AUT65MAP_outsideCPB_tenmins
              ,AUC65MAP_preCPB_mmHgtenmins
              ,AUC65MAP_postCPB_mmHgtenmins              
              )

# Creating variables in 10 min intervals
relevant_data$duration_Surgery_tenmins<-relevant_data$duration_Surgery_min/10
relevant_data$duration_CPB_tenmins<-relevant_data$duration_CPB_min/10
relevant_data$duration_outsideCPB_tenmins<-relevant_data$duration_outsideCPB_min/10

# mean centering and standardizing AUC
relevant_data$AUC65MAP_total_mmHgtenmins_std<-meancstand(relevant_data$AUC65MAP_total_mmHgtenmins)
```

## Export dataset analyzed

```{r}
write.csv(relevant_data,'relevant_data.csv',row.names = F)
```


# Factorizing Variables

```{r}
# Other variables to be factorized
relevant_data$Gender<-as.factor(relevant_data$Gender)
relevant_data$Category<-as.factor(relevant_data$Category)
relevant_data$Anesthesiologist<-as.factor(relevant_data$Anesthesiologist)

# Outcomes
relevant_data$Any_MAE<-as.factor(relevant_data$Any_MAE)
relevant_data$Renal_Failure<-as.factor(relevant_data$Renal_Failure)
relevant_data$Stroke<-as.factor(relevant_data$Stroke)
relevant_data$Death<-as.factor(relevant_data$Death)
relevant_data$RFDS<-as.factor(relevant_data$RFDS)

relevant_data$IOH_cat<-as.factor(relevant_data$IOH_cat)

relevant_data$Q_AUT65MAP_CPB_IOH_ratio<-as.factor(relevant_data$Q_AUT65MAP_CPB_IOH_ratio)


# Factorizing Quarrtiles
relevant_data$Q_AUT50MAP_total_min<-as.factor(relevant_data$Q_AUT50MAP_total_min)
relevant_data$Q_AUT65MAP_total_min<-as.factor(relevant_data$Q_AUT65MAP_total_min)
relevant_data$Q_AUT65MAP_total_min<-as.factor(relevant_data$Q_AUT65MAP_total_min)
relevant_data$Q_AOT65MAP_total_min<-as.factor(relevant_data$Q_AOT65MAP_total_min)
relevant_data$Q_total_pressors_formula_mg<-as.factor(relevant_data$Q_total_pressors_formula_mg)
relevant_data$Q_AUC65MAP_total_mmHgmin<-as.factor(relevant_data$Q_AUC65MAP_total_mmHgmin)
relevant_data$Q_AOC65MAP_total_mmHgmin<-as.factor(relevant_data$Q_AOC65MAP_total_mmHgmin)
relevant_data$Q_TWA65MAP_total_mmHg<-as.factor(relevant_data$Q_TWA65MAP_total_mmHg)
relevant_data$Q_TWA65MAP_outsideCPB_mmHg<-as.factor(relevant_data$Q_TWA65MAP_outsideCPB_mmHg)
relevant_data$Q_AUC65MAP_outsideCPB_mmHgmin<-as.factor(relevant_data$Q_AUC65MAP_outsideCPB_mmHgmin)
relevant_data$Q_TWA65MAP_CPB_mmHg<-as.factor(relevant_data$Q_TWA65MAP_CPB_mmHg)
relevant_data$Q_AUC65MAP_CPB_mmHgmin<-as.factor(relevant_data$Q_AUC65MAP_CPB_mmHgmin)

relevant_data$Q_AUT65MAP_total_min<-as.factor(relevant_data$Q_AUT65MAP_total_min)

# Factorizing Tertiles
relevant_data$T_STS_RiskAlgorithm_median_imp<-as.factor(relevant_data$T_STS_RiskAlgorithm_median_imp)
relevant_data$T_STS_RiskAlgorithm_multiple_imp<-as.factor(relevant_data$T_STS_RiskAlgorithm_multiple_imp)

#relevant_data$Q_AUT80SBP_total_min<-as.factor(relevant_data$Q_AUT80SBP_total_min)

# Factorizing tertiles
# relevant_data$T_AUT50MAP_total_min<-as.factor(relevant_data$T_AUT50MAP_total_min)
# relevant_data$T_AUT65MAP_total_min<-as.factor(relevant_data$T_AUT65MAP_total_min)
# relevant_data$T_AOT65MAP_total_min<-as.factor(relevant_data$T_AOT65MAP_total_min)
# relevant_data$T_total_pressors_formula_mg<-as.factor(relevant_data$T_total_pressors_formula_mg)

#relevant_data$Anesthesiologist<-as.factor(relevant_data$Anesthesiologist)

# creating T_STS_RiskAlgorithm_median_imp variable

# Selecting reference levels for the categorical variables
relevant_data$Gender <- relevel(relevant_data$Gender, ref = "Male")
relevant_data$Category <- relevel(relevant_data$Category, ref = "CAB+other")


```

# TEST 1 Full Cohort

## Full Surgery Duration

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.  
Exposure: Duration of total hypotension.

```{r}
relevant_data$old_pressors<-relevant_data$total_pressors_formula_mg+relevant_data$milrinone

mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_total_tenmins
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_tenmins
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)

print('VIF Analysis')
vif(mod_multiv)

ggeffect(mod_multiv,terms="AUT65MAP_total_tenmins") %>% plot()


oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"Predicted RFDS"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table

oddsratios_table %>%
  kbl(caption = "Odds Ratio" , align = "c") %>%
  kable_classic_2(full_width = F, html_font = "Cambria")
```

##### AU the ROC and precision-recall curve

```{r fig.height=4.5, fig.width=9}
par(mfrow = c(1, 2))
AUC(mod_multiv, main = "ROC curve")
AUC(mod_multiv, curve = "PR", main = "Precision-recall curve")
```


### Exploratory analyses

####  Exploratory analysis 1

Outcome: Renal_Failure  
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_total_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1

```

####  Exploratory analysis 2

Outcome: Death.  
Exposure: main exposure AUT65MAP_total_min.  

```{r}
# Selecting reference levels for the categorical variables
relevant_data$Gender <- relevel(relevant_data$Gender, ref = "Male")

mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_total_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

####  Exploratory analysis 3

Outcome: Stroke.  
Exposure: main exposure AUT65MAP_total_min.  

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_total_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)

oddsratios_table
```

## CPB

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_CPB_tenmins
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_tenmins
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"Predicted RFDS"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1

oddsratios_table %>%
  kbl(caption = "Odds Ratio" , align = "c") %>%
  kable_classic_2(full_width = F, html_font = "Cambria")
```

### Exploratory analyses

####  Exploratory analysis 1

Outcome: Renal Failure.  
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_CPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

####  Exploratory analysis 2

Outcome: Death.  
Exposure: main exposure AUT65MAP_total_min.  

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_CPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table

```

####  Exploratory analysis 3

Outcome: Stroke.  
Exposure: main exposure AUT65MAP_total_min.  

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_CPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

## outsideCPB

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_outsideCPB_tenmins
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_tenmins
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"Predicted RFDS"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table %>%
  kbl(caption = "Odds Ratio" , align = "c") %>%
  kable_classic_2(full_width = F, html_font = "Cambria")
```

### Exploratory analyses

####  Exploratory analysis 1

Outcome: Stroke
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_outsideCPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

####  Exploratory analysis 2

Outcome: Renal Failure
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables
relevant_data$Gender <- relevel(relevant_data$Gender, ref = "Male")

mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_outsideCPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table

```

####  Exploratory analysis 3

Outcome: Death
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_outsideCPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

# Sensitivity analysis

Creating sensitivity dataset.
We are only including cases with *AUT65MAP_total_min < 0.95 Quantile*.

```{r}
below_ninetyfith<-relevant_data[relevant_data$AUT65MAP_total_min < quantile(relevant_data$AUT65MAP_total_min, 0.95), ]
```

## Full Surgery Duration adressed

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_total_min
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = below_ninetyfith
            , family=binomial(link="logit"))

summary(mod_multiv)

ggeffect(mod_multiv,terms="AUT65MAP_total_min") %>% plot()




oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"Predicted RFDS"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1

oddsratios_table
```

### Exploratory analyses

####  Exploratory analysis 1

Outcome: Renal Failure.  
Exposure: main exposure AUT65MAP_total_min.  

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_total_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

####  Exploratory analysis 2

Outcome: Death.  
Exposure: main exposure AUT65MAP_total_min.  

```{r}
mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_total_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1

oddsratios_table
```

####  Exploratory analysis 3

Outcome: Stroke.  
Exposure: main exposure AUT65MAP_total_min.  

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_total_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)

oddsratios_table

```

## CPB

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_CPB_min
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = below_ninetyfith
            , family=binomial(link="logit"))

summary(mod_multiv)


oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"Predicted RFDS"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1

oddsratios_table
```

### Exploratory analyses

####  Exploratory analysis 1

Outcome: Stroke
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_CPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)

oddsratios_table
```

####  Exploratory analysis 2

Outcome: Renal Failure
Exposure: main exposure AUT65MAP_total_min

```{r}
mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_CPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table
```

####  Exploratory analysis 3

Outcome: Death
Exposure: main exposure AUT65MAP_total_min

```{r}
mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_CPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table
```
## outsideCPB

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_outsideCPB_min
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = below_ninetyfith
            , family=binomial(link="logit"))

summary(mod_multiv)

ggeffect(mod_multiv,terms="AUT65MAP_outsideCPB_min") %>% plot()




oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"Predicted RFDS"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table
```

### Exploratory analyses

####  Exploratory analysis 1

Outcome: Stroke
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_outsideCPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table
```

####  Exploratory analysis 2

Outcome: Renal Failure
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables
sen_analysis_data$Gender <- relevel(sen_analysis_data$Gender, ref = "Male")

mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_outsideCPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1

oddsratios_table
```

####  Exploratory analysis 3

Outcome: Death
Exposure: main exposure AUT65MAP_total_min

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUT65MAP_outsideCPB_min
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = below_ninetyfith
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1


oddsratios_table
```

# TEST 2 IOH Cat as main exposure

# Full Cohort

## Full Surgery Duration

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
relevant_data$IOH_cat <- relevel(relevant_data$IOH_cat, ref = "1")


mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + IOH_cat
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)



oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"Predicted RFDS"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table

```








### Exploratory analyses





####  Exploratory analysis 1

Outcome: Stroke
Exposure: main exposure IOH_cat

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +IOH_cat
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)

oddsratios_table

```

####  Exploratory analysis 2

Outcome: Renal Failure
Exposure: main exposure IOH_cat

```{r}
# Selecting reference levels for the categorical variables


mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +IOH_cat
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table

```

####  Exploratory analysis 3

Outcome: Death
Exposure: main exposure IOH_cat

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +IOH_cat
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
oddsratios_table

```


# TEST 3 Full Cohort 

## Full AUC

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUC65MAP_total_mmHgtenmins_std
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)

#ggeffect(mod_multiv,terms="AUC65MAP_total_mmHgmin") %>% plot()




oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table


oddsratios_table %>%
  kbl(caption = "Odds Ratio" , align = "c") %>%
  kable_classic_2(full_width = F, html_font = "Cambria")

```

### Exploratory analyses

####  Exploratory analysis 1

Outcome: Stroke
Exposure: main exposure AUC65MAP_total_mmHgmin

```{r}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Renal_Failure ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUC65MAP_total_mmHgmin
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

####  Exploratory analysis 2

Outcome: Renal Failure
Exposure: main exposure AUC65MAP_total_mmHgmin

```{r}
# Selecting reference levels for the categorical variables
relevant_data$Gender <- relevel(relevant_data$Gender, ref = "Male")

mod_multiv<-glm(Death ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUC65MAP_total_mmHgmin
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

####  Exploratory analysis 3

Outcome: Death
Exposure: main exposure AUC65MAP_total_mmHgmin

```{r warning=FALSE}
# Selecting reference levels for the categorical variables

mod_multiv<-glm(Stroke ~ 
                 +total_pressors_formula_mg
                 +milrinone
                 +AUC65MAP_total_mmHgmin
                 +T_STS_RiskAlgorithm_multiple_imp
                 +Gender
                 +Age
                 +Category
                 +delta_HCT_pct_median_imp
                 +mean_ef_median_imp
                 +duration_Surgery_min
                 +Cross_Clamp_Time_imp
                 ,family='binomial'
                 ,data = relevant_data
                )

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table

```

# TEST 4 Full Cohort STS Continous

## Full AUT

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_total_min
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + T_STS_RiskAlgorithm_multiple_imp
                 + Cross_Clamp_Time_imp
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)

#ggeffect(mod_multiv,terms="AUT65MAP_total_min") %>% plot()




oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```

# TEST 5 Full Cohort instead of STS we use comorbid variables

## Full AUT

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUT65MAP_total_min
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + Diabetes                        
                 + Hypertension_final             
                 + Congestive_Heart_Failure       
                 + Previous_myocardial_infarction 
                 + ChronicLungDisease             
                 + Dialysis                       
                 + PreOpMedBetaBlockers           
                 + PreOpMedInotropes              
                 + PreOpMedSteroids               
                 + PreOpMedAspirin                
                 + PreOpMedLipidLowering          
                 + duration_CPB_min         
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)

#ggeffect(mod_multiv,terms="AUT65MAP_total_min") %>% plot()




oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table
```




# TEST 6 Full Cohort instead of STS we use comorbid variables

## Full AUC

###  Primary analyses

#### Primary analysis 1

Outcome: composite variable of death, stroke, renal failure.
Exposure: Duration of total hypotension.

```{r}
mod_multiv<-glm(RFDS ~ 
                   total_pressors_formula_mg
                 + AUC65MAP_total_mmHgmin
                 + milrinone
                 + Gender
                 + Age
                 + Category
                 + delta_HCT_pct_median_imp
                 + mean_ef_median_imp
                 + duration_Surgery_min
                 + Diabetes                        
                 + Hypertension_final             
                 + Congestive_Heart_Failure       
                 + Previous_myocardial_infarction 
                 + ChronicLungDisease             
                 + Dialysis                       
                 + PreOpMedBetaBlockers           
                 + PreOpMedInotropes              
                 + PreOpMedSteroids               
                 + PreOpMedAspirin                
                 + PreOpMedLipidLowering          
                 + duration_CPB_min         
                 , data = relevant_data
            , family=binomial(link="logit"))

summary(mod_multiv)

oddsratios_table<-exp(cbind(coef(mod_multiv), confint(mod_multiv)))  
options(scipen=999)
oddsratios_table<-round(oddsratios_table,4)
#oddsratios_table['x']<-(1:10)

oddsratios_table<-as.data.frame(oddsratios_table)
colnames(oddsratios_table)[1]<-"OR"

oddsratios_table<-oddsratios_table[order(row.names(oddsratios_table)), ]
boxLabels<-rownames(oddsratios_table)
#oddsratios_table['yAxis']<- length(boxLabels):1
oddsratios_table

```






